### 2024-06-21 presentations/presentation_fevrier/presentation_fevrier.tex
Ajout des présentations et des figures

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation
% LaTeX Template
% Version 2.0 (March 8, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	11pt, % Set the default font size, options include: 8pt, 9pt, 10pt, 11pt, 12pt, 14pt, 17pt, 20pt
	%t, % Uncomment to vertically align all slide content to the top of the slide, rather than the default centered
	%aspectratio=169, % Uncomment to set the aspect ratio to a 16:9 ratio which matches the aspect ratio of 1080p and 4K screens and projectors
]{beamer}

\graphicspath{{Images/}{./}} % Specifies where to look for included images (trailing slash required)

\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule for better rules in tables

%----------------------------------------------------------------------------------------
%	SELECT LAYOUT THEME
%----------------------------------------------------------------------------------------

% Beamer comes with a number of default layout themes which change the colors and layouts of slides. Below is a list of all themes available, uncomment each in turn to see what they look like.

%\usetheme{default}
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{Dresden}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

%----------------------------------------------------------------------------------------
%	SELECT COLOR THEME
%----------------------------------------------------------------------------------------

% Beamer comes with a number of color themes that can be applied to any layout theme to change its colors. Uncomment each of these in turn to see how they change the colors of your selected layout theme.

%\usecolortheme{albatross}
%\usecolortheme{beaver}
%\usecolortheme{beetle}
%\usecolortheme{crane}
%\usecolortheme{dolphin}
%\usecolortheme{dove}
%\usecolortheme{fly}
%\usecolortheme{lily}
%\usecolortheme{monarca}
%\usecolortheme{seagull}
%\usecolortheme{seahorse}
%\usecolortheme{spruce}
%\usecolortheme{whale}
%\usecolortheme{wolverine}

%----------------------------------------------------------------------------------------
%	SELECT FONT THEME & FONTS
%----------------------------------------------------------------------------------------

% Beamer comes with several font themes to easily change the fonts used in various parts of the presentation. Review the comments beside each one to decide if you would like to use it. Note that additional options can be specified for several of these font themes, consult the beamer documentation for more information.

\usefonttheme{default} % Typeset using the default sans serif font
%\usefonttheme{serif} % Typeset using the default serif font (make sure a sans font isn't being set as the default font if you use this option!)
%\usefonttheme{structurebold} % Typeset important structure text (titles, headlines, footlines, sidebar, etc) in bold
%\usefonttheme{structureitalicserif} % Typeset important structure text (titles, headlines, footlines, sidebar, etc) in italic serif
%\usefonttheme{structuresmallcapsserif} % Typeset important structure text (titles, headlines, footlines, sidebar, etc) in small caps serif

%------------------------------------------------

%\usepackage{mathptmx} % Use the Times font for serif text
\usepackage{palatino} % Use the Palatino font for serif text

%\usepackage{helvet} % Use the Helvetica font for sans serif text
\usepackage[default]{opensans} % Use the Open Sans font for sans serif text
%\usepackage[default]{FiraSans} % Use the Fira Sans font for sans serif text
%\usepackage[default]{lato} % Use the Lato font for sans serif text
\usepackage[yyyymmdd]{datetime}

%----------------------------------------------------------------------------------------
%	SELECT INNER THEME
%----------------------------------------------------------------------------------------

% Inner themes change the styling of internal slide elements, for example: bullet points, blocks, bibliography entries, title pages, theorems, etc. Uncomment each theme in turn to see what changes it makes to your presentation.

%\useinnertheme{default}
\useinnertheme{circles}
%\useinnertheme{rectangles}
%\useinnertheme{rounded}
%\useinnertheme{inmargin}

%----------------------------------------------------------------------------------------
%	SELECT OUTER THEME
%----------------------------------------------------------------------------------------

% Outer themes change the overall layout of slides, such as: header and footer lines, sidebars and slide titles. Uncomment each theme in turn to see what changes it makes to your presentation.

%\useoutertheme{default}
%\useoutertheme{infolines}
%\useoutertheme{miniframes}
%\useoutertheme{smoothbars}
%\useoutertheme{sidebar}
%\useoutertheme{split}
%\useoutertheme{shadow}
%\useoutertheme{tree}
%\useoutertheme{smoothtree}

%\setbeamertemplate{footline} % Uncomment this line to remove the footer line in all slides
%\setbeamertemplate{footline}[page number] % Uncomment this line to replace the footer line in all slides with a simple slide count

%\setbeamertemplate{navigation symbols}{} % Uncomment this line to remove the navigation symbols from the bottom of all slides

%----------------------------------------------------------------------------------------
%	PRESENTATION INFORMATION
%----------------------------------------------------------------------------------------

\title[Initation Recherche]{Création de différentes IA en utilisant une architecture I2A} % The short title in the optional parameter appears at the bottom of every slide, the full title in the main parameter is only on the title page

\subtitle{Dans le contexte du jeu Sokoban} % Presentation subtitle, remove this command if a subtitle isn't required

\author[Thomas Guyomard / Jérémy Tremblay]{Thomas Guyomard - Jérémy Tremblay} % Presenter name(s), the optional parameter can contain a shortened version to appear on the bottom of every slide, while the main parameter will appear on the title slide

\institute[]{Université du Littoral Côte d'Opale\\ \smallskip \textit{Encadrant : Jérôme Buisine}} % Your institution, the optional parameter can be used for the institution shorthand and will appear on the bottom of every slide after author names, while the required parameter is used on the title slide and can include your email address or additional information on separate lines

\date[\today]{\today} % Presentation date or conference/meeting name, the optional parameter can contain a shortened version to appear on the bottom of every slide, while the required parameter value is output to the title slide

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SLIDE
%----------------------------------------------------------------------------------------

\begin{frame}
	\titlepage % Output the title slide, automatically created using the text entered in the PRESENTATION INFORMATION block above
\end{frame}

%----------------------------------------------------------------------------------------
%	TABLE OF CONTENTS SLIDE
%----------------------------------------------------------------------------------------

% The table of contents outputs the sections and subsections that appear in your presentation, specified with the standard \section and \subsection commands. You may either display all sections and subsections on one slide with \tableofcontents, or display each section at a time on subsequent slides with \tableofcontents[pausesections]. The latter is useful if you want to step through each section and mention what you will discuss.

\begin{frame}
	\frametitle{Sommaire} % Slide title, remove this command for no title

	\tableofcontents % Output the table of contents (all sections on one slide)
	%\tableofcontents[pausesections] % Output the table of contents (break sections up across separate slides)
\end{frame}

%----------------------------------------------------------------------------------------
%	PRESENTATION BODY SLIDES
%----------------------------------------------------------------------------------------

 % Sections are added in order to organize your presentation into discrete blocks, all sections and subsections are automatically output to the table of contents as an overview of the talk but NOT output in the presentation as separate slides

%------------------------------------------------

\section{Références}

\begin{frame}
	\frametitle{Références}

	Sébastien Racanière, Théophane Weber, David P. Reichert, Lars Buesing, Arthur Guez, Danilo Rezende, Adria Puigdomènech Badia, Oriol Vinyals, Nicolas Heess, Yujia Li, Razvan Pascanu, Peter Battaglia, Demis Hassabis, David Silver, Daan Wierstra, "Imagination-Augmented Agents for Deep Reinforcement Learning", DeepMind, arXiv:1707.06203v2 [cs.LG] 14 Feb 2018

\end{frame}

%------------------------------------------------
\section{Présentation du jeu Sokoban}

\begin{frame}
	\frametitle{Présentation du jeu Sokoban}

	Jeu de \alert{réflexion}. Le but : le joueur doit ranger des caisses sur des cases cibles.
	\smallskip % Vertical whitespace

	\begin{itemize}
		\item Le personnage a la capacité d'effectuer des déplacement dans chacune des 4 directions possibles. Le niveau est validé une fois toutes les caisses rangées.
	\end{itemize}

	\smallskip % Vertical whitespace

	\begin{figure}
		\includegraphics[width=0.2\linewidth]{Images/sokaibanfailed2.png}
		\caption{Capture d'écran du jeu Sokoban.}
	\end{figure}

\end{frame}

%------------------------------------------------
\section{Agents Augmentés par l'Imagination}

\begin{frame}
	\frametitle{Agents Augmentés par l'Imagination \ / (I2A)}

	\smallskip % Vertical whitespace

	\begin{definition}
	\alert{L'apprentissage par renforcement avec augmentation par l'imagination} appelée \alert{I2A} est une approche du domaine de l'intelligence artificielle permettant d'améliorer la prise de décision des agents d'apprentissage.
	Les agents combinent l'apprentissage automatique avec et sans modèles avec des générations de scénarios pour anticiper des situations inédites et proposer des solutions optimales.
	\end{definition}

	\smallskip % Vertical whitespace

\end{frame}

%------------------------------------------------

\section{IA Q-learning avec une représentation en tableau}

\begin{frame}
	\frametitle{IA Q-learning avec une représentation en tableau}

	\begin{block}{Definitions}
		L'implémentation combine le Q-learning avec un modèle interne I2A pour résoudre le problème complexe du Sokoban, un jeu de réflexion.
	\end{block}

	\smallskip % Vertical whitespace

	\begin{figure}
		\includegraphics[width=0.5\linewidth]{Images/q_learning.png}
		\caption{Schéma du fonctionnement du Q-Learning.}
	\end{figure}

\end{frame}
%------------------------------------------------
\section{Ajout d'un mécanisme de renforcement}

\begin{frame}{Ajout d'un mécanisme de renforcement}
    \begin{itemize}
        \item \textbf{Application du renforcement au jeu du Sokoban}
            \begin{itemize}
                \item L'agent (IA) apprend à jouer au Sokoban en interagissant avec l'environnement.
                \item Les récompenses définies pour différentes actions guident l'agent vers des comportements souhaités.
            \end{itemize}
        \item \textbf{Mise en application du Q-Learning}
            \begin{itemize}
                \item La Q-table est mise à jour itérativement en fonction des récompenses obtenues.
                \item L'agent utilise la Q-table pour choisir ses actions et optimiser sa politique de choix au fil du temps.
            \end{itemize}
    \end{itemize}
\end{frame}
%------------------------------------------------
\section{Implémentation du Q-learning}

\begin{frame}
	\frametitle{Implémentation du Q-learning}

	\begin{itemize}
        \item \textbf{Q-table} Contient les états / actions du jeu, elle est initialisée avec des zéros.
        \item \textbf{Boucle d'apprentissage} Itérations sur des épisodes pour mettre à jour la Q-table.
        \item \textbf{Système de récompenses} Intégration des récompenses conformément à la politique définie.
        \item \textbf{Mise à jour de la \textbf \textit Q-table} Prise en compte de la récompense immédiate et de l'estimation de la récompense future.
        \item \textbf{Exploration et Exploitation} Equilibre les connaissances actuelles et permet davantage d'apprentissage.
    \end{itemize}

\end{frame}
%------------------------------------------------

\section{Intégration du système de récompense}

\begin{frame}
	\frametitle{Intégration du système de récompense}

	\begin{block}{Objectif}
		Introduire un système de récompenses permettant de guider l'agent vers les actions optimales grâce à des récompenses positives et des pénalités.
	\end{block}

	\smallskip % Vertical whitespace

	\begin{center}
        \begin{tabular}{|c|c|}
            \hline
            \textbf{Action} & \textbf{Récompense} \\
            \hline
            Effectuer une action & -0.1 \\
            Pousser une boîte sur la cible & 1.0 \\
            Pousser une boîte hors de la cible & -1.0 \\
            Achever le niveau & 10.0 \\
            \hline
        \end{tabular}
    \end{center}

	\begin{block}{Pour aller plus loin...}
		Pénalités en cas de caisses bloquées.
	\end{block}
\end{frame}

%------------------------------------------------

\section{Résultats}

\begin{frame}
	\frametitle{Résultats}

	\begin{itemize}
        \item \textbf{Un temps d'exécution élevé} Concernant la génération des niveaux.
        \item \textbf{Des performances faibles...} Valeurs des récompenses négatives à la fin de l'execution et constantes: -300.
        \item \textbf{Des niveaux différents} Rendant l'apprentissage caduc.
        \item \textbf{Représentation de la partie} On cherche à récupérer un visuel du jeu afin de réaliser un I2A et d'améliorer le système de récompenses.
    \end{itemize}
\end{frame}

%------------------------------------------------
\section{Plan de Travail}

\begin{frame}{Plan de Travail}
    \begin{table}
        \centering
		\small
        \begin{tabular}{|c|p{8cm}|}
			\hline
            1 & Résolution des probleme de performances et apprentissage plus poussé. \\
            \hline
            2 & Comparaison des performances avec des modèles comme MCTS pour évaluer l'efficacité relative. \\
            \hline
            3 & Si possible, explorer la possibilité d'utiliser les représentations visuelles de Gym Sokoban pour enrichir la planification. \\
            \hline
            4 & Tester l'agent sur différents niveaux afin d'évaluer sa capacité de généralisation. \\
            \hline
            5 & Analyser les performances de chaque approche, en mettant en évidence les forces et les faiblesses dans le contexte de Sokoban. \\
            \hline
        \end{tabular}
    \end{table}
\end{frame}

%----------------------------------------------------------------------------------------
%	CLOSING SLIDE
%----------------------------------------------------------------------------------------

\begin{frame}[plain] % The optional argument 'plain' hides the headline and footline
	\begin{center}
		{\Huge Merci pour votre attention.}

	\end{center}
\end{frame}
%----------------------------------------------------------------------------------------

\end{document}

### 2024-06-21 presentations/article/article.tex
Add search article template

\documentclass[12pt]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[margin=0.9in]{geometry}
\usepackage{multicol}

\usepackage{csquotes}
\usepackage[style=verbose-ibid,backend=biber]{biblatex}
\bibliography{sample}

\title{How to use axions to shine light through walls}

\author{Nicholas Montague}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
The axion is a hypothetical particle, introduced by the Peccei-Quinn theory in 1977 as a solution to the strong CP problem in quantum chromodynamics. The axion, if it exists, must have a very small mass, and must be very weakly interacting with baryonic matter, giving it the abbreviation WISP (Weakly Interacting Sub-ev Particle). The predicted attributes of the axion would give it the ability to pass directly through an opaque wall without obstruction, and this is how the ALPS experiment (Any Light Particle Search) at DESY in Hamburg is exploring the possibility of their existence. In this report, we will use matrix methods to reproduce the relationship between axion mass and axion coupling as published by the ALPS experiment \autocite{Ehret, K. et al (2010). New ALPS results on hidden-sector lightweights} in 2010, using their conversion probability to plot the result. Note that all equations, unless otherwise stated, are in natural units ($c=1$, $\hbar = 1$).
\end{abstract}

\section{Introduction}

In particle physics, there is a lot of speculation over why quantum chromodynamics (QCD) does not seem to break CP-symmetry in the strong interaction \autocite{Peccei, R.D. (2006). The Strong CP Problem and Axions} when it should. CP-symmetry is the idea that if we take a system, perform charge conjugation so that all particles become their antiparticles, and also 'flip' the system so that all lefts become rights and vice-versa, the laws of physics remain unchanged. A way to overcome this problem, is to promote the CP violating parameter to a new field, called the axion field, and introduce its propagating particle, the axion. By introducing this new particle, the QCD Lagrangian is altered slightly, as this accounts for the error in the CP-symmetry. 
The axion is also of great interest to the standard model, as if its mass lies in a certain low range, it is a possible component for cold dark matter \autocite{Duffy, L.D., Bibber, K. (2009). Axions as Dark Matter Particles}  that has been observed, but not identified. The two criteria that must be satisfied to be a possible dark matter candidate are: (1) a very cold population of axions could be present in our universe in large enough quantities to provide the required dark matter energy density and (2) they are effectively collisionless. There have been several experiments that have attempted to detect the presence of axions, using a range of predicted properties of axions. 
One these was the Polarizzazione del Vuoto con LASer (PVLAS) in Italy, with ideas put forward by Luciano Maiani, Roberto Petronzio and Emilio Zavattini in 1986 \autocite{Maiani, L., Petronzio, R., Zavattini, E.(1986). Effects of nearly massless, spin-zero particles on light propagation in a magnetic field}. PVLAS searches for a slight rotation in the polarisation plane of light shining through a strong electromagnetic field. One interpretation \autocite{Ringwald, D. (2006). Axion interpretation of the PVLAS data?} of this effect includes the production of a small particle (an axion) with a mass $m_a~meV$ which couples to a pair of photons.
Another experiment is the Axion Dark Matter Experiment\autocite{Duffy, L.D. et al. (2006). A High Resolution Search for Dark-Matter Axions} (ADMX) at the University of Washington, which searches for axions in the local galactic dark matter halo using a microwave cavity detector. Although no axion signal was found, they were able to place a limit on the mass of the axion, between $1.98-2.17 \mu eV$. 
The particular experiment that we will be concentrating on, is the "Light Shining Through Walls" experiment (LSW), in particular, results published by the ALPS Collaboration at the Deutsches Elektronen-Synchrotron in Hamburg, in the paper 'New ALPS results on hidden-sector lightweights' \autocite{Ehret, K. et al (2010). New ALPS results on hidden-sector lightweights}. They were able to place limits on the probability of photon-axion-photon conversions to a very high precision $(10^{-25})$.

\section{Theory}
\label{sec:theory}

A LSW experiment takes advantage of the fact that axions are very weakly interacting to detect their presence. The experimental setup of the ALPS collaboration consists of a $4.4m$ long vacuum chamber heading directly into a wall, and the equivalent on the other side of the wall (see 1) \autocite{http://inspirehep.net/record/791128/plots, 07/05/2014}. A strong magnetic field is applied perpendicular to the vacuum tubes, and a laser emits a beam of photons through the magnetic field. At a photon-photon vertex, when two photons interact with each other, they can couple, which leads to the production of an axion. As the axion is very weakly interacting, it can pass directly through the opaque wall, whereas all the photons are absorbed or reflected by it. On the other side of the wall, the axion can decay into two photons, in a reverse way to how it was created. If the detector on the right picks up any photons, this means that light has seemed to have travelled through the wall, but infact it is another, weakly interacting particle that has surpassed the wall, most probably an axion.

\begin{figure}[h]=
\centering
\includegraphics[width=0.7\textwidth]{Images/sokoban_cas_1.png}
\caption{\label{fig:RMPfig23.jpg}This diagram shows a simple layout for the LSW experiment. Taken from inspirehep.net}
\end{figure}

For the ALPS experiment, a $5T$ magnetic field was used, provided by a HERA superconducting dipole magnet, and the photons were produced by a $532nm$ laser. In order to increase the power of the laser (to improve the conversion probability), the laser was shone through a potassium titanyl phosphate (PPKTP) crystal. However this high intensity of the fundamental frequencies also caused second and higher order modes to increase in intensity. By reducing the waist size of the system, the second order harmonic beam can be reduced by a factor of 100, whereas the first order harmonic is only reduced by a factor of 15. They were limited to using a laser power of $5W$, as when this was increased to $8W$, an effect called gray-tracking was detected in the setup.
After several 10 hours of the laser running, the power build-up started to degrade. This was found to be due to a slight degradation in the quality of mirrors used to direct the laser beam. 
Obviously a perfect vacuum is not achievable in a laboratory. The two vacuum chambers were filled with $99.9995\%$ pure argon, which has a refractive index close to one. The relative change of the refractive index in the chambers was estimated to produce a negligable error.
It was important that the structure of the system was very stable and rigid, especially on the light tight box with the detector and camera in, as these had to be removed to access the wall in the centre. The camera had to be posioned very precisely each time it was removed, and this error was determined to be less than $6\mu m$. 
Future improvements to the ALPS experiment include increasing the length of the vacuum chambers, directly increasing the probability that a conversion will occur in the increased distance, and also increasing the magnetic field strength across the vacuum chambers. 2017 hopes to see the completion of ALPS-IIc \autocite{https://alps.desy.de/e141064, 11/05/2014}, with a 100 metre long cavity on either side of the wall, and magnets covering this entire distance.

\section{Method}
\label{sec:method}

Start with a stationary wave equation for particles propagating along the z axis of a system,

\begin{equation}
\left(\omega^2+\partial_z^2+\left( \begin{array}{ccc}
Q_{perp} & 0 & 0 \\
0 & Q_{para} & {\frac{B\omega}{M}} \\
0 & {\frac{B\omega}{M}} & -m_a^2 \end{array} \right)\ \right)\
\left( \begin{array}{c} 
A_{perp} \\ 
A_{para} \\
a \end{array} \right) = 0 
\end{equation}

where $\omega$ is the frequency of light, $Q_{j} = 2\omega^2(n_j-1)$, $n_j$ is the refractive index in the $j$ direction, $B$ is the transverse part of the magnetic field strength, $M$ is inversely proportional to the coupling strength and $m_a$ is the axion mass. $A_{perp}, A_{para}$ and $a$ are the perpendicular and parallel amplitudes of the photon states and the amplitude of the axion state respectively. This differential equation will prove difficult to solve, as there are three coupled equations in three different dimensions.

\subsection{Simplification to Two Dimensions}

A simplification can be made for the term $(\omega^2 + \partial_z^2)$ by factorising into $(\omega+i\partial_z)(\omega-i\partial_z)$, and noticing that, in natural units, $i\partial_z = k$. At this point, an approximation may be introduced, by assuming that the refractive index is equal to that of a vacuum, so $n\approx 1$, and $k=n\omega$ resulting in $k\approx\omega$.
Applying this approximation and dividing through by $2\omega$, \textbf{(1)} may be rewritten,

\begin{equation}
\left(\omega+\left( \begin{array}{ccc}
\Delta_{perp} & 0 & 0 \\
0 & \Delta_{para} & \Delta_M \\
0 & \Delta_M & \Delta_a \end{array} \right)-i\partial_z\right)\
\left( \begin{array}{c} 
A_{perp} \\ 
A_{para} \\
a \end{array} \right) = 0 
\end{equation}

where all $\Delta's$ are the previous matrix elements reduced by $2\omega$.
As the only interest is in the parallel photon (going towards the wall) and the axion field, $A_{perp}$ and the $\Delta_{perp}$ row and column can be neglected, and the system can be described by the $2x2$ matrix equation,

\begin{equation}
\left(\omega+\left( \begin{array}{ccc}
\Delta_{para} & \Delta_M \\
\Delta_M & \Delta_a \end{array} \right)
-i\partial_z \right)
\left( \begin{array}{ccc} 
A_{para} \\
a \end{array} \right) = 0
\end{equation}

As this is a two dimensional matrix equation, all terms must be matrices, and the non-matrix variables may be written as products of the identity matrix, so they become

\begin{equation*}
\left( \begin{array}{ccc}
\omega & 0 \\
0 & \omega \end{array} \right) and 
\left( \begin{array}{ccc}
i\partial_z & 0 \\
\ 0 & i\partial_z \end{array} \right)
\end{equation*}

Notice that the approximation of $n\approx 1$ means that $Q_j = 2\omega^2(n_j-1)\approx 0$, so $\Delta_{para}$ can be neglected, and some simple rearranging yields the two dimensional differential matrix equation

\begin{equation}
i\partial_z \left( \begin{array}{ccc}
A_{para} \\
a \end{array} \right) = \left( \begin{array}{ccc}
\omega & \frac{B}{2M} \\
\frac{B}{2M} & \omega-\frac{m_a^2}{2\omega} \end{array} \right)
\left( \begin{array}{ccc}
A_{para} \\
a \end{array} \right)
\end{equation}

This gives two coupled differential equations, which are still not simple and straightforward to solve, as they are still coupled to each other.

\subsection{Diagonalisation of the Matrix}

A matrix can be written as a product of its eigenvectors and its diagonalised matrix, in the form $\textbf{A} = \textbf{PDP}^{-1}$, where $\textbf{P}$ and $\textbf{P}^{-1}$ are eigenvectors of $\textbf{A}$,

\begin{equation*}
\textbf{D} = \left( \begin{array}{ccc}
d_1 & 0 \\
0 & d_2 \end{array} \right)
\end{equation*}

and, in this case, $\textbf{A}$ is the 2x2 matrix from equation $(4)$, 
\\
\begin{equation*}
\textbf{A} = \left( \begin{array}{ccc} \omega & \frac{B}{2M} \\ \frac{B}{2M} & 
\omega-\frac{m_a^2}{2\omega} \end{array} \right)
\end{equation*}
\\
With a matrix in its diagonalised form, there are no longer any cross-terms in the matrix multiplication, meaning that, for equation $(4)$, the differential equations will no longer be coupled to each other, and will become much easier to solve. By diagonalising the 2x2 matrix, equation $(4)$ will be able to be rewritten in the form

\begin{equation}
i\frac{\partial}{\partial_z} \left( \begin{array}{ccc} x_1 \\ x_2 \end{array} \right) = \left( \begin{array}{ccc} d_1 & 0 \\ 0 & d_2 \end{array} \right) \left( \begin{array}{ccc} x_1 \\ x_2 \end{array} \right)
\end{equation}

where $d_1$ and $d_2$ are the eigenvalues, and $x_1$ and $x_2$ are the components of the matrix $\textbf{X}$ defined by $\textbf{X} = \textbf{P}^{-1} \left( \begin{array}{ccc} A_{perp} \\ a \end{array} \right)$.

\subsection{Finding the Eigenvalues}

To find the eigenvalues of the matrix, use the equation

\begin{equation}
\left| \begin{array}{ccc}
\omega - \lambda & \frac{B}{2M} \\
\frac{B}{2M} & \omega - \frac{m_a^2}{2\omega} - \lambda \end{array} \right| = 0
\end{equation}

Solving this for $\lambda$, and using the quadratic equation, yields the unsightly result

\begin{equation}
\lambda = \frac{2\omega - \frac{m_a^2}{2\omega}\pm \sqrt{1+\frac{4B^2\omega^2}{M^2m_a^4}}}{2}
\end{equation}

However, we can define $tan2\theta = \frac{2B\omega}{Mm_a^2}$ and using the substitution $1+tan^2\theta = sec^2\theta$, reduces equation$(7)$ to

\begin{equation}
\lambda = \omega \pm \frac{m_a^2}{4\omega} (sec2\theta \mp 1)
\end{equation}

Next, notice that $sec2\theta-1 = \frac{2sin^2\theta}{cos2\theta}$ and $sec2\theta+1 = \frac{2cos^2\theta}{cos2\theta}$, so the two eigenvalues, $\lambda_+$ and $\lambda_-$, can be written,

\begin{equation}
\lambda_+ = \omega + \frac{m_a^2sin^2\theta}{2\omega cos2\theta} \ and \  
\lambda_- = \omega - \frac{m_a^2cos^2\theta}{2\omega cos2\theta}
\end{equation}
\
so the final diagonalised matrix is as follows:

\begin{equation*}
\left( \begin{array}{ccc} 
\omega + \frac{m_a^2sin^2\theta}{2\omega cos2\theta} & 0 \\
0 & \omega - \frac{m_a^2cos^2\theta}{2\omega cos2\theta} \end{array} \right)
\end{equation*}

\subsection{Finding the Eigenvectors}

To find the eigenvectors, solve the eigenvalue equation,

\begin{equation}
\left ( \begin{array}{ccc} 
\omega & \frac{B}{2M} \\
\frac{B}{2M} & \omega-\frac{m_a^2}{2\omega} \end{array} \right)
\left( \begin{array}{ccc}
\alpha & \beta \\
\gamma & \delta \end{array} \right) 
=\left ( \begin{array}{ccc} 
\lambda_+ & 0 \\
0 & \lambda_- \end{array} \right)
\left( \begin{array}{ccc}
\alpha & \beta \\
\gamma & \delta \end{array} \right)
\end{equation}

to gain a relationship between $\alpha$, $\beta$, $\gamma$ and $\delta$.
By carrying out the matrix multiplication, and fiddling around with trigonometric functions, we reach two relationships,

\begin{equation*}
\frac{\gamma}{\alpha} = tan\theta \ and \ \frac{\beta}{\delta} = -tan\theta
\end{equation*}

which leads to eigenvectors, previously labelled $\textbf{P}$, and its inverse, $\textbf{P}^{-1}$:

\begin{equation*}
\textbf{P} = \left( \begin{array}{ccc}
cos\theta & -sin\theta \\
sin\theta & cos\theta \end{array} \right) \ and \ 
\textbf{P}^{-1} = \left( \begin{array}{ccc}
cos\theta & sin\theta \\
-sin\theta & cos\theta \end{array} \right)
\end{equation*}

\subsection{Working out Probabilities}
Now, $x_1$ and $x_2$ from equation $(5)$ can simply be calculated by

\begin{equation}
\left( \begin{array}{ccc} x_1 \\ x_2 \end{array} \right) = \left( \begin{array}{ccc} cos\theta & sin\theta \\
-sin\theta & cos\theta \end{array} \right) 
\left( \begin{array}{ccc} A_{para} \\ a \end{array} \right)
\end{equation}
so $x_1 = A_{para}cos\theta + asin\theta$ and $x_2 = acos\theta - A_{para}sin\theta$. We now have all the necessary numbers that we need to plug into equation $(5)$. By solving the two differential equations in equation $(5)$ serperately, we obtain two more equations for $x_1$ and $x_2$ in the form $ x_1 = \mu e^{-i\lambda_+z}$ and $x_2 = \nu e^{-i\lambda_-z}$ where $\mu$ and $\nu$ are constants of integration. At $z=0$, when the beam is initially created, it is made entirely of photons, and no axions, so initally $A_{para}=1$ and $a=0$. Seperating $\mu$ and $\nu$ from the exponential terms, from equation $(11)$ we can derive the equation

\begin{equation}
\left( \begin{array}{ccc} A_{para}(z) \\ a(z) \end{array} \right) =
\left( \begin{array}{ccc} cos\theta & -sin\theta \\ sin\theta & cos\theta \end{array} \right)
\left( \begin{array}{ccc} e^{-i\lambda_+z } & 0 \\ 0 & e^{-i\lambda_-z} \end{array} \right) 
\left( \begin{array}{ccc} \mu \\ \nu \end{array} \right)
\end{equation}

By investigating equation$(12)$ at the point $z=0$, the constants $\mu$ and $\nu$ can be found, so can be rewritten as a product of $ \textbf{P}^{-1}$ and the field amplitudes at $z=0$. This allows equation $(12)$ to be simplified to

\begin{equation}
\left( \begin{array}{ccc} A_{para}(z) \\ a(z) \end{array} \right) =
\textbf{M} \left( \begin{array}{ccc} A_{para}(0) \\ a(0) \end{array} \right)
\end{equation}

where $\textbf{M}$ is defined by

\begin{equation}
\begin{array}{ccc}
\textbf{M} = \left( \begin{array}{ccc} cos\theta & -sin\theta \\ sin\theta & cos\theta \end{array} \right)
\left( \begin{array}{ccc} e^{-i\lambda_+z} & 0 \\ 0 & e^{-i\lambda_-z} \end{array} \right)
\left( \begin{array}{ccc} cos\theta & sin\theta \\ -sin\theta & cos\theta \end{array} \right) \\
\\
= \left( \begin{array}{ccc} e_-sin^2\theta + e_+cos^2\theta & (e_+-e_-)sin\theta cos\theta \\ 
(e_+-e_-)sin\theta cos\theta & e_+sin^2\theta + e_-cos^2\theta \end{array} \right)
\end{array}
\end{equation}
where $e_+$ and $e_-$ are $e^{-i\lambda_+z}$ and $e^{-i\lambda_-z}$ respectively.
Equation $(13)$ can now give the probability amplitude of the photon and axion fields at any point on the z-axis, simply by inputting the z-coordinate, and this means that the modulus square of the individual matrix elements gives a probability. E.g. ${\left|{M_{12}}\right|}^2 = Prob(p\rightarrow a)$. The particular equations that we are interested in are the probability that a photon will couple with an axion, and that an axion will couple with a photon, corresponding to the matrix elements $M_{12}$ and $M_{21}$, which happen to be identical to each other, and equal to

\begin{equation}
Prob(p\rightarrow a) = Prob(a\rightarrow p) = \left| e_+-e_- \right|^2 sin^2\theta cos^2\theta
\end{equation}

\subsection{Large and Small Axion Mass Approximations}
Equation $(15)$ is not of great help, as the exponential terms still depend on both the axion mass and coupling, so it is difficult to directly evaluate the relationship between the two. However, we can make large and small mass approximations, where we investigate the behaviour of the equations, if we assume the axion has a very small mass, and if it has a very large mass. Before making any approximations, manipulate equation $(15)$ using variations of trigonometric identities, so that $sin^2\theta cos^2\theta$ becomes $\frac{sin^22\theta}{4}$, and convert the exponential terms into a $cos$ term, so it becomes

\begin{equation}
Prob = \left( 1 - cos[(\lambda_+-\lambda_-)z] \right) \frac{sin^22\theta}{2}
\end{equation}
Now the only parts of equation $(16)$ that depend on either the axion mass or the axion coupling are the trigonometric functions, so we can apply the approximations to the $sin^22\theta$, as it is of a higher power. By writing

\begin{equation*}
tan^22\theta = \frac{4B^2\omega^2}{M^2m_a^4} = \frac{sin^22\theta}{cos^22\theta} = \frac{sin^22\theta}{1-sin^22\theta}
\end{equation*}

we can rearrange for $sin^22\theta$, and write this as a fraction of constants (known and unknown).

\begin{equation}
sin^22\theta = \frac{4B^2\omega^2}{M^2m_a^4+4B^2\omega^2}
\end{equation}

This is where an approximation can be introduced. If the axion mass, $m_a$, is taken to be very small, $(m_a<<1)$, then $m_a^4$ can be neglected and assumed to be zero. This leads to, for small mass, $sin^22\theta \approx 1$. If the axion mass is taken to be very large, the $m_a^4$ term becomes very large, $4B^2\omega^2$ can be neglected and $sin^22\theta \approx \frac{4B^2\omega^2}{M^2m_a^4}$. When plugged into equation $(16)$, substituting in the constants for ($\lambda_+-\lambda_-$), we get the probability for the small mass limit:

\begin{equation}
Prob = \frac{1}{2} \left[ 1-cos\left(\frac{m_a^2z}{2\omega cos2\theta} \right) \right]
\end{equation}

By writing $cos2\theta$ in terms of constants, and again making another small $m_a$ approximation and neglecting a 1, we find $cos2\theta \approx \frac{Mm_a^2}{2B\omega}$, so equation $(18)$ becomes

\begin{equation} Prob = \frac{1}{2} \left[ 1-cos \left(\frac{Bz}{M} \right) \right]
\end{equation}
Equation $(19)$ shows that in the small mass limit, the probability that a photon becomes an axion or vice-versa, does not depend at all on the mass of the axion. This is convenient as it makes the mass-coupling relationship much easier to plot, simply as a straight line.

In the large mass limit, $sin^22\theta \approx \frac{4B^2\omega^2}{M^2m_a^4}$ so following the same method as for in the low mass limit, but approximating $cos2\theta \approx 1$, we get the result

\begin{equation} Prob = \frac{1}{2} \left[ 1- cos\left(\frac{m_a^2z}{2\omega} \right) \right] \frac{4B^2\omega^2}{M^2m_a^4}
\end{equation}

\section{Results}
\label{sec:results}

By using the results published in the 2010 'New ALPS results on hidden-sector lightweights' (this paper will be referred to several times in the results and discussions), we read that the maximum conversion probability from photon, to axion, to photon again is, in the $95\%$ probability limit, $2.25\times10^{-25}$. So the probability of a single conversion is the square root of this. By using this value in equation $(19)$ and equation $(20)$, we acquire two different relationships between axion mass, $m_a$, and coupling $1/M$, one for a high mass and one for a low mass. Figure (2) shows these two relationships plotted on a graph. 
\begin{figure}[h]
\centering
\includegraphics[width=1\textwidth]{Images/sokoban_cas_2.png}
\caption{\label{Graph.jpg} A graph showing the boundary of the relationship between the axion mass and axion coupling.}
\end{figure}

The left hand side of the graph (the flat line) is a graphical representation of the fact that, if the mass is very small, the coupling becomes independent of the mass of the axion. The right hand side of the graph shows that, if the mass is significantly large, the limit becomes dependent on a decaying trigonometric function. These results match up with figure 4 from the 'New ALPS results...' paper. This line does not, however, represent the only values that the mass and coupling can take,  as we recall that the probability of conversion used is the \textit{maximum} probability. Therefore, this line only represents a boundary between possible and im possible combinations of axion mass and coupling values, and rules out any combinations of values that lie above the line. Also notice that, for a low mass, figure 2 reads a coupling strength of $\approx 2\times 10^{-8} GeV^{-1} $, whereas, in figure 4 of the ALPS paper previously mentioned, the low mass coupling strength reads to be $\approx 5\times 10^{-7}GeV{-1}$. We see, in figure 2 that the large mass approximation starts to have effect at around $10^{-12} GeV$, which matches up very closely with figure 4 of the ALPS paper.

\section{Discussion}
\label{sec:discussion}
The difference in the two values for the low mass coupling strength may have been caused by a number of factors. Firsly, an assumption has been made, that, because $g \propto 1/M$, $g = 1/M$. No account has been made of a possible constant factor in the case where $g$ and $M$ are not directly inversely proportional.
Another error may have arisen due to the fact that we assumed that the quoted probability, $2.25 \times 10^{-25}$, was the probability that a photon $\rightarrow$ axion $\rightarrow$ photon conversion would take place, where it may have actually been that a single photon $\rightarrow$ axion / axion $\rightarrow$ photon conversion would occur. 
Some small errors may have also been introduced when converting constants, such as the magnetic field or the frequency of light, into electron volts to be in natural units. The constants, in natural units, were inputted to only 4 decimal places. To improve the accuracy of the values on the graph plotted in figure 2, these constants could be used to many more decimal places, especially when using an accurate program, such as MatLab. 
We must however take figure 2 with a pinch of salt, as there is obviously a large transition step between the small mass and large mass approximations. The closer the values are to the transition between the two approximations, the more unreliable the values are, as the original fraction we were using to approximate in equation $(17)$ becomes less dependent on just a single term of the denominator. 
Another assumption that has been made is that the refractive index inside the argon gas is equal to that of a vacuum, $n=1$, whereas the real refractive index is slightly higher than this.

\section{Conclusions}
\label{sec:conclusions}

In this experiment, we have theoretically reproduced limits set on the mass and coupling strength of possible axionic particles, by using a series of mathematical calculations and physical and mathematical approximations. Our methods and approximations have arrived at a graph which qualitatively matches the most stringent constraints on the existence of axions. \\
In the future, the ALPS collaboration will continue with their research into the properties of axions and other weakly interacting particles, by increasing magnet strength and laser power, to increase the chances of photon $\rightarrow$ axion conversion.

\printbibliography

\end{document}

### 2024-06-22 presentations/article/article.tex
Add article and first sections

@@
-\documentclass[12pt]{article}
+\documentclass[10pt,twocolumn]{article}
 
@@
 
-\title{How to use axions to shine light through walls}
+\title{Using Q-Learning in Sokoban: Performance Enhancements and Challenges}
 
-\author{Nicholas Montague}
+\author{
+  J. Tremblay\textsuperscript{1}\thanks{\texttt{jeremy-tremblay@outlook.fr}}  
+  \space et T. Guyomard\textsuperscript{1}\thanks{\texttt{thomas.guyomard@etu.univ-littoral.fr}} \\
+  \textsuperscript{1}Université du Littoral Côte d'Opale, Calais, France
+}
 
@@
 \begin{abstract}
-The axion is a hypothetical particle, introduced by the Peccei-Quinn theory in 1977 as a solution to the strong CP problem in quantum chromodynamics.
-The axion, if it exists, must have a very small mass, and must be very weakly interacting with baryonic matter, giving it the abbreviation WISP (Weakly Interacting Sub-ev Particle).
-The predicted attributes of the axion would give it the ability to pass directly through an opaque wall without obstruction, and this is how the ALPS experiment (Any Light Particle Search) at DESY in Hamburg is exploring the possibility of their existence.
-In this report, we will use matrix methods to reproduce the relationship between axion mass and axion coupling as published by the ALPS experiment \autocite{Ehret, K.
-et al (2010).
-New ALPS results on hidden-sector lightweights} in 2010, using their conversion probability to plot the result.
-Note that all equations, unless otherwise stated, are in natural units ($c=1$, $\hbar = 1$).
+    This paper explores the application of Q-Learning to the game Sokoban, focusing on various performance enhancements and challenges encountered.
+Despite its simplicity, Sokoban presents significant challenges for reinforcement learning algorithms due to its complex state space and delayed rewards.
+We developed several versions of a Q-Learning algorithm with modifications such as wall detection, elimination of unnecessary actions, and reward system adjustments.
+Experimental results demonstrate varying degrees of improvement in performance with these enhancements.
+However, one of the primary limitations encountered was the particularly long training times required for effective learning.
+Our findings provide insights into the limitations and potential of Q-Learning in Sokoban, highlighting areas for future research and application.
 \end{abstract}
@@
 
-In particle physics, there is a lot of speculation over why quantum chromodynamics (QCD) does not seem to break CP-symmetry in the strong interaction \autocite{Peccei, R.D.
-(2006).
-The Strong CP Problem and Axions} when it should.
-CP-symmetry is the idea that if we take a system, perform charge conjugation so that all particles become their antiparticles, and also 'flip' the system so that all lefts become rights and vice-versa, the laws of physics remain unchanged.
-A way to overcome this problem, is to promote the CP violating parameter to a new field, called the axion field, and introduce its propagating particle, the axion.
-By introducing this new particle, the QCD Lagrangian is altered slightly, as this accounts for the error in the CP-symmetry.
-The axion is also of great interest to the standard model, as if its mass lies in a certain low range, it is a possible component for cold dark matter \autocite{Duffy, L.D., Bibber, K.
-(2009).
-Axions as Dark Matter Particles}  that has been observed, but not identified.
-The two criteria that must be satisfied to be a possible dark matter candidate are: (1) a very cold population of axions could be present in our universe in large enough quantities to provide the required dark matter energy density and (2) they are effectively collisionless.
-There have been several experiments that have attempted to detect the presence of axions, using a range of predicted properties of axions.
-One these was the Polarizzazione del Vuoto con LASer (PVLAS) in Italy, with ideas put forward by Luciano Maiani, Roberto Petronzio and Emilio Zavattini in 1986 \autocite{Maiani, L., Petronzio, R., Zavattini, E.(1986).
-Effects of nearly massless, spin-zero particles on light propagation in a magnetic field}.
-PVLAS searches for a slight rotation in the polarisation plane of light shining through a strong electromagnetic field.
-One interpretation \autocite{Ringwald, D.
-(2006).
-Axion interpretation of the PVLAS data?} of this effect includes the production of a small particle (an axion) with a mass $m_a~meV$ which couples to a pair of photons.
-Another experiment is the Axion Dark Matter Experiment\autocite{Duffy, L.D.
-et al.
-(2006).
-A High Resolution Search for Dark-Matter Axions} (ADMX) at the University of Washington, which searches for axions in the local galactic dark matter halo using a microwave cavity detector.
-Although no axion signal was found, they were able to place a limit on the mass of the axion, between $1.98-2.17 \mu eV$.
-The particular experiment that we will be concentrating on, is the "Light Shining Through Walls" experiment (LSW), in particular, results published by the ALPS Collaboration at the Deutsches Elektronen-Synchrotron in Hamburg, in the paper 'New ALPS results on hidden-sector lightweights' \autocite{Ehret, K.
-et al (2010).
-New ALPS results on hidden-sector lightweights}.
-They were able to place limits on the probability of photon-axion-photon conversions to a very high precision $(10^{-25})$.
+Reinforcement learning (RL), a branch of machine learning, has transformed how algorithms learn to make decisions by interacting with environments to maximize cumulative rewards.
+Among RL techniques, Q-Learning stands out for its simplicity and effectiveness in learning optimal policies through iterative trial and error.
 
-\section{Theory}
-\label{sec:theory}
+Adapted extensively in video games, Q-Learning excels in environments where decisions influence future states and outcomes.
+Sokoban, a classic puzzle game where players push boxes to designated locations, presents unique challenges for reinforcement learning algorithms due to its vast state space and delayed rewards.
+Each action in Sokoban can have intricate consequences, making effective strategy learning challenging without extensive training and fine-tuning.
 
-A LSW experiment takes advantage of the fact that axions are very weakly interacting to detect their presence.
-The experimental setup of the ALPS collaboration consists of a $4.4m$ long vacuum chamber heading directly into a wall, and the equivalent on the other side of the wall (see 1) \autocite{http://inspirehep.net/record/791128/plots, 07/05/2014}.
-A strong magnetic field is applied perpendicular to the vacuum tubes, and a laser emits a beam of photons through the magnetic field.
-At a photon-photon vertex, when two photons interact with each other, they can couple, which leads to the production of an axion.
-As the axion is very weakly interacting, it can pass directly through the opaque wall, whereas all the photons are absorbed or reflected by it.
-On the other side of the wall, the axion can decay into two photons, in a reverse way to how it was created.
-If the detector on the right picks up any photons, this means that light has seemed to have travelled through the wall, but infact it is another, weakly interacting particle that has surpassed the wall, most probably an axion.
+This study explores these challenges and aims to enhance Q-Learning's effectiveness in Sokoban through modifications such as wall detection, action reduction, and adjustments to the reward system.
+Despite advancements, a significant limitation encountered is the extended training times necessary for effective learning.
+These findings contribute to understanding Q-Learning in complex environments, suggesting avenues for future research and practical applications.
 
-\begin{figure}[h]=
+\section{Related Works}
+
+Previous studies have demonstrated the effectiveness of Q-Learning and deep reinforcement learning techniques in various gaming environments.
+Mnih et al.
+(2013) pioneered the use of deep Q-Learning to learn game policies directly from pixel inputs, achieving human-level performance on multiple classic Atari games.
+
+In the realm of real-time strategy games, Vinyals et al.
+(2019) showcased advanced Q-Learning and reinforcement learning methods in achieving Grandmaster level performance in StarCraft II.
+Their work exemplifies the application of sophisticated learning algorithms to master complex strategic environments.
+
+These studies highlight the versatility of Q-Learning in adapting to diverse gaming dynamics, from classic Atari games to complex real-time strategy scenarios like StarCraft II.
+In contrast, the challenges specific to Sokoban, such as sparse rewards and intricate state transitions, remain less explored.
+This study aims to address these challenges and enhance Q-Learning's applicability in puzzle-solving domains.
+
+\section{Theoretical Foundations}
+
+\subsection{Q-Learning Basics}
+
+Q-Learning is a reinforcement learning technique used to learn optimal actions to take in a given state to maximize cumulative rewards.
+At its core, Q-Learning maintains a Q-Table (or Q-Function), denoted as \( Q(s, a) \), where \( s \) represents a state and \( a \) an action.
+The table is updated iteratively based on the Bellman equation:
+
+\[
+    Q(s, a) \leftarrow (1 - \alpha) \cdot Q(s, a) + \alpha \cdot \left( r + \gamma \cdot \max_{a'} Q(s', a') \right)
+\]
+
+Here, \\
+- \( \alpha \) (learning rate) controls how much new information overrides old information. \\
+- \( \gamma \) (discount factor) determines the importance of future rewards. \\
+- \( r \) is the immediate reward received after taking action \( a \) in state \( s \). \\
+- \( s' \) is the resulting state after taking action \( a \). \\
+
+The Q-Table stores the expected future rewards for all state-action pairs, guiding the agent's decision-making process during exploration and exploitation phases.
+
+\subsection{Exploration-Exploitation Trade-off}
+
+In Q-Learning, \( \epsilon \) controls the exploration-exploitation trade-off, crucial for learning optimal strategies in dynamic environments.
+The \( \epsilon \)-greedy policy dictates action selection:
+
+\[
+    \pi(a|s) =
+    \begin{cases}
+        1 - \epsilon + \frac{\epsilon}{|\mathcal{A}(s)|}, & \text{if } a = \arg\max_{a'} Q(s, a') \\
+        \frac{\epsilon}{|\mathcal{A}(s)|},                & \text{otherwise}
+    \end{cases}
+\]
+
+Here, \( Q(s, a) \) denotes the Q-value of action \( a \) in state \( s \), \( \mathcal{A}(s) \) represents the set of possible actions in state \( s \), and \( |\mathcal{A}(s)| \) is the number of actions available in state \( s \).
+
+Initially set high (e.g., 1.0), \( \epsilon \) encourages exploration early in training. As training progresses, \( \epsilon \) is generally reduced to prioritize exploitation of learned actions.
+
+\subsection{Implementation Details}
+
+In our implementation, we focused on guiding the agent's behavior through a carefully designed reward system.
+The system was crucial in reinforcing desired actions, such as pushing boxes onto targets, while discouraging undesired actions like pushing boxes off targets.
+These rewards were iteratively adjusted to improve the agent's learning process and performance in solving the Sokoban puzzle efficiently.
+
+State representation involved converting the Sokoban map into a numerical format to ensure state uniqueness and reduce complexity.
+This approach facilitated effective learning and decision-making by the Q-Learning algorithm.
+
+\section{Methodology}
+
+\subsection{Tools}
+
+The implementation was conducted using Python programming language, leveraging the Gym Sokoban library.
+Gym Sokoban provides a simulated environment for the Sokoban game, facilitating the integration of reinforcement learning algorithms for experimentation and evaluation.
+
+\subsection{Initialization of Q-Learning}
+
+To evaluate the effectiveness of Q-Learning in the Sokoban game context, we began by implementing a basic Q-Learning algorithm using the Gym Sokoban library in Python.
+The Q-Table was initialized with default parameters ($\alpha$ = 0.5, $\gamma$ = 0.95, $\epsilon$ = 0.1).
+
+\subsection{Reward System}
+
+The initial reward system was defined as follows:
+\begin{itemize}
+    \item Performing an action: -0.1
+    \item Pushing a box onto a target: +1.0
+    \item Pushing a box off target: -1.0
+    \item All boxes on targets: +10.0
+\end{itemize}
+
+\subsection{State Representation}
+
+To ensure state uniqueness, we converted the Sokoban map into a numerical representation and hashed it to obtain a unique state identifier.
+This approach reduced state complexity while preserving uniqueness.
+
+\subsection{Iterative Improvements}
+
+We introduced several modifications to enhance Q-Learning performance:
+\begin{itemize}
+    \item Detection of losing conditions to avoid ineffective actions.
+    \item Restriction of the "do nothing" action to promote active movements.
+    \item Optimization of alpha, gamma, and epsilon parameters, as well as the reward system, to improve learning.
+\end{itemize}
+
+\subsection{Generalization Evaluation}
+
+We evaluated the model's ability to generalize to new Sokoban levels by testing its performance without complete retraining.
+This methodology enabled us to explore the capabilities and limitations of Q-Learning in a complex gaming environment.
+
+\section{Implementation and Results}
+
+\subsection{Initial Q-Learning Implementation}
+
+We began by implementing Q-Learning on a Sokoban puzzle with three boxes using the Gym Sokoban library in Python.
+The chosen level (Figure \ref{fig:sokoban_level}) is a representative example of Sokoban's complexity, where the agent must strategically move 3 boxes to designated target locations.
+
+\begin{figure}[ht]
     \centering
-\includegraphics[width=0.7\textwidth]{Images/sokoban_cas_1.png}
-\caption{\label{fig:RMPfig23.jpg}This diagram shows a simple layout for the LSW experiment. Taken from inspirehep.net}
+    \includegraphics[width=0.3\textwidth]{Images/sokoban.png}
+    \caption{Example Sokoban level used for these Q-Learning experiments.}
+    \label{fig:sokoban_level}
 \end{figure}
 
-For the ALPS experiment, a $5T$ magnetic field was used, provided by a HERA superconducting dipole magnet, and the photons were produced by a $532nm$ laser.
-In order to increase the power of the laser (to improve the conversion probability), the laser was shone through a potassium titanyl phosphate (PPKTP) crystal.
-However this high intensity of the fundamental frequencies also caused second and higher order modes to increase in intensity.
-By reducing the waist size of the system, the second order harmonic beam can be reduced by a factor of 100, whereas the first order harmonic is only reduced by a factor of 15.
-They were limited to using a laser power of $5W$, as when this was increased to $8W$, an effect called gray-tracking was detected in the setup.
-After several 10 hours of the laser running, the power build-up started to degrade. This was found to be due to a slight degradation in the quality of mirrors used to direct the laser beam. 
-Obviously a perfect vacuum is not achievable in a laboratory.
-The two vacuum chambers were filled with $99.9995\%$ pure argon, which has a refractive index close to one.
-The relative change of the refractive index in the chambers was estimated to produce a negligable error.
-It was important that the structure of the system was very stable and rigid, especially on the light tight box with the detector and camera in, as these had to be removed to access the wall in the centre.
-The camera had to be posioned very precisely each time it was removed, and this error was determined to be less than $6\mu m$.
-Future improvements to the ALPS experiment include increasing the length of the vacuum chambers, directly increasing the probability that a conversion will occur in the increased distance, and also increasing the magnetic field strength across the vacuum chambers.
-2017 hopes to see the completion of ALPS-IIc \autocite{https://alps.desy.de/e141064, 11/05/2014}, with a 100 metre long cavity on either side of the wall, and magnets covering this entire distance.
-
-\section{Method}
-\label{sec:method}
-
-Start with a stationary wave equation for particles propagating along the z axis of a system,
-
-\begin{equation}
-\left(\omega^2+\partial_z^2+\left( \begin{array}{ccc}
-Q_{perp} & 0 & 0 \\
-0 & Q_{para} & {\frac{B\omega}{M}} \\
-0 & {\frac{B\omega}{M}} & -m_a^2 \end{array} \right)\ \right)\
-\left( \begin{array}{c} 
-A_{perp} \\ 
-A_{para} \\
-a \end{array} \right) = 0 
-\end{equation}
-
-where $\omega$ is the frequency of light, $Q_{j} = 2\omega^2(n_j-1)$, $n_j$ is the refractive index in the $j$ direction, $B$ is the transverse part of the magnetic field strength, $M$ is inversely proportional to the coupling strength and $m_a$ is the axion mass.
-$A_{perp}, A_{para}$ and $a$ are the perpendicular and parallel amplitudes of the photon states and the amplitude of the axion state respectively.
-This differential equation will prove difficult to solve, as there are three coupled equations in three different dimensions.
-
-\subsection{Simplification to Two Dimensions}
-
-A simplification can be made for the term $(\omega^2 + \partial_z^2)$ by factorising into $(\omega+i\partial_z)(\omega-i\partial_z)$, and noticing that, in natural units, $i\partial_z = k$.
-At this point, an approximation may be introduced, by assuming that the refractive index is equal to that of a vacuum, so $n\approx 1$, and $k=n\omega$ resulting in $k\approx\omega$.
-Applying this approximation and dividing through by $2\omega$, \textbf{(1)} may be rewritten,
-
-\begin{equation}
-\left(\omega+\left( \begin{array}{ccc}
-\Delta_{perp} & 0 & 0 \\
-0 & \Delta_{para} & \Delta_M \\
-0 & \Delta_M & \Delta_a \end{array} \right)-i\partial_z\right)\
-\left( \begin{array}{c} 
-A_{perp} \\ 
-A_{para} \\
-a \end{array} \right) = 0 
-\end{equation}
-
-where all $\Delta's$ are the previous matrix elements reduced by $2\omega$.
-As the only interest is in the parallel photon (going towards the wall) and the axion field, $A_{perp}$ and the $\Delta_{perp}$ row and column can be neglected, and the system can be described by the $2x2$ matrix equation,
-
-\begin{equation}
-\left(\omega+\left( \begin{array}{ccc}
-\Delta_{para} & \Delta_M \\
-\Delta_M & \Delta_a \end{array} \right)
--i\partial_z \right)
-\left( \begin{array}{ccc} 
-A_{para} \\
-a \end{array} \right) = 0
-\end{equation}
-
-As this is a two dimensional matrix equation, all terms must be matrices, and the non-matrix variables may be written as products of the identity matrix, so they become
-
-\begin{equation*}
-\left( \begin{array}{ccc}
-\omega & 0 \\
-0 & \omega \end{array} \right) and 
-\left( \begin{array}{ccc}
-i\partial_z & 0 \\
-\ 0 & i\partial_z \end{array} \right)
-\end{equation*}
-
-Notice that the approximation of $n\approx 1$ means that $Q_j = 2\omega^2(n_j-1)\approx 0$, so $\Delta_{para}$ can be neglected, and some simple rearranging yields the two dimensional differential matrix equation
-
-\begin{equation}
-i\partial_z \left( \begin{array}{ccc}
-A_{para} \\
-a \end{array} \right) = \left( \begin{array}{ccc}
-\omega & \frac{B}{2M} \\
-\frac{B}{2M} & \omega-\frac{m_a^2}{2\omega} \end{array} \right)
-\left( \begin{array}{ccc}
-A_{para} \\
-a \end{array} \right)
-\end{equation}
-
-This gives two coupled differential equations, which are still not simple and straightforward to solve, as they are still coupled to each other.
-
-\subsection{Diagonalisation of the Matrix}
-
-A matrix can be written as a product of its eigenvectors and its diagonalised matrix, in the form $\textbf{A} = \textbf{PDP}^{-1}$, where $\textbf{P}$ and $\textbf{P}^{-1}$ are eigenvectors of $\textbf{A}$,
-
-\begin{equation*}
-\textbf{D} = \left( \begin{array}{ccc}
-d_1 & 0 \\
-0 & d_2 \end{array} \right)
-\end{equation*}
-
-and, in this case, $\textbf{A}$ is the 2x2 matrix from equation $(4)$, 
-\\
-\begin{equation*}
-\textbf{A} = \left( \begin{array}{ccc} \omega & \frac{B}{2M} \\ \frac{B}{2M} & 
-\omega-\frac{m_a^2}{2\omega} \end{array} \right)
-\end{equation*}
-\\
-With a matrix in its diagonalised form, there are no longer any cross-terms in the matrix multiplication, meaning that, for equation $(4)$, the differential equations will no longer be coupled to each other, and will become much easier to solve.
-By diagonalising the 2x2 matrix, equation $(4)$ will be able to be rewritten in the form
-
-\begin{equation}
-i\frac{\partial}{\partial_z} \left( \begin{array}{ccc} x_1 \\ x_2 \end{array} \right) = \left( \begin{array}{ccc} d_1 & 0 \\ 0 & d_2 \end{array} \right) \left( \begin{array}{ccc} x_1 \\ x_2 \end{array} \right)
-\end{equation}
-
-where $d_1$ and $d_2$ are the eigenvalues, and $x_1$ and $x_2$ are the components of the matrix $\textbf{X}$ defined by $\textbf{X} = \textbf{P}^{-1} \left( \begin{array}{ccc} A_{perp} \\ a \end{array} \right)$.
-
-\subsection{Finding the Eigenvalues}
-
-To find the eigenvalues of the matrix, use the equation
-
-\begin{equation}
-\left| \begin{array}{ccc}
-\omega - \lambda & \frac{B}{2M} \\
-\frac{B}{2M} & \omega - \frac{m_a^2}{2\omega} - \lambda \end{array} \right| = 0
-\end{equation}
-
-Solving this for $\lambda$, and using the quadratic equation, yields the unsightly result
-
-\begin{equation}
-\lambda = \frac{2\omega - \frac{m_a^2}{2\omega}\pm \sqrt{1+\frac{4B^2\omega^2}{M^2m_a^4}}}{2}
-\end{equation}
-
-However, we can define $tan2\theta = \frac{2B\omega}{Mm_a^2}$ and using the substitution $1+tan^2\theta = sec^2\theta$, reduces equation$(7)$ to
-
-\begin{equation}
-\lambda = \omega \pm \frac{m_a^2}{4\omega} (sec2\theta \mp 1)
-\end{equation}
-
-Next, notice that $sec2\theta-1 = \frac{2sin^2\theta}{cos2\theta}$ and $sec2\theta+1 = \frac{2cos^2\theta}{cos2\theta}$, so the two eigenvalues, $\lambda_+$ and $\lambda_-$, can be written,
-
-\begin{equation}
-\lambda_+ = \omega + \frac{m_a^2sin^2\theta}{2\omega cos2\theta} \ and \  
-\lambda_- = \omega - \frac{m_a^2cos^2\theta}{2\omega cos2\theta}
-\end{equation}
-\
-so the final diagonalised matrix is as follows:
-
-\begin{equation*}
-\left( \begin{array}{ccc} 
-\omega + \frac{m_a^2sin^2\theta}{2\omega cos2\theta} & 0 \\
-0 & \omega - \frac{m_a^2cos^2\theta}{2\omega cos2\theta} \end{array} \right)
-\end{equation*}
-
-\subsection{Finding the Eigenvectors}
-
-To find the eigenvectors, solve the eigenvalue equation,
-
-\begin{equation}
-\left ( \begin{array}{ccc} 
-\omega & \frac{B}{2M} \\
-\frac{B}{2M} & \omega-\frac{m_a^2}{2\omega} \end{array} \right)
-\left( \begin{array}{ccc}
-\alpha & \beta \\
-\gamma & \delta \end{array} \right) 
-=\left ( \begin{array}{ccc} 
-\lambda_+ & 0 \\
-0 & \lambda_- \end{array} \right)
-\left( \begin{array}{ccc}
-\alpha & \beta \\
-\gamma & \delta \end{array} \right)
-\end{equation}
-
-to gain a relationship between $\alpha$, $\beta$, $\gamma$ and $\delta$.
-By carrying out the matrix multiplication, and fiddling around with trigonometric functions, we reach two relationships,
-
-\begin{equation*}
-\frac{\gamma}{\alpha} = tan\theta \ and \ \frac{\beta}{\delta} = -tan\theta
-\end{equation*}
-
-which leads to eigenvectors, previously labelled $\textbf{P}$, and its inverse, $\textbf{P}^{-1}$:
-
-\begin{equation*}
-\textbf{P} = \left( \begin{array}{ccc}
-cos\theta & -sin\theta \\
-sin\theta & cos\theta \end{array} \right) \ and \ 
-\textbf{P}^{-1} = \left( \begin{array}{ccc}
-cos\theta & sin\theta \\
--sin\theta & cos\theta \end{array} \right)
-\end{equation*}
-
-\subsection{Working out Probabilities}
-Now, $x_1$ and $x_2$ from equation $(5)$ can simply be calculated by
-
-\begin{equation}
-\left( \begin{array}{ccc} x_1 \\ x_2 \end{array} \right) = \left( \begin{array}{ccc} cos\theta & sin\theta \\
--sin\theta & cos\theta \end{array} \right) 
-\left( \begin{array}{ccc} A_{para} \\ a \end{array} \right)
-\end{equation}
-so $x_1 = A_{para}cos\theta + asin\theta$ and $x_2 = acos\theta - A_{para}sin\theta$.
-We now have all the necessary numbers that we need to plug into equation $(5)$.
-By solving the two differential equations in equation $(5)$ serperately, we obtain two more equations for $x_1$ and $x_2$ in the form $ x_1 = \mu e^{-i\lambda_+z}$ and $x_2 = \nu e^{-i\lambda_-z}$ where $\mu$ and $\nu$ are constants of integration.
-At $z=0$, when the beam is initially created, it is made entirely of photons, and no axions, so initally $A_{para}=1$ and $a=0$.
-Seperating $\mu$ and $\nu$ from the exponential terms, from equation $(11)$ we can derive the equation
-
-\begin{equation}
-\left( \begin{array}{ccc} A_{para}(z) \\ a(z) \end{array} \right) =
-\left( \begin{array}{ccc} cos\theta & -sin\theta \\ sin\theta & cos\theta \end{array} \right)
-\left( \begin{array}{ccc} e^{-i\lambda_+z } & 0 \\ 0 & e^{-i\lambda_-z} \end{array} \right) 
-\left( \begin{array}{ccc} \mu \\ \nu \end{array} \right)
-\end{equation}
-
-By investigating equation$(12)$ at the point $z=0$, the constants $\mu$ and $\nu$ can be found, so can be rewritten as a product of $ \textbf{P}^{-1}$ and the field amplitudes at $z=0$.
-This allows equation $(12)$ to be simplified to
-
-\begin{equation}
-\left( \begin{array}{ccc} A_{para}(z) \\ a(z) \end{array} \right) =
-\textbf{M} \left( \begin{array}{ccc} A_{para}(0) \\ a(0) \end{array} \right)
-\end{equation}
-
-where $\textbf{M}$ is defined by
-
-\begin{equation}
-\begin{array}{ccc}
-\textbf{M} = \left( \begin{array}{ccc} cos\theta & -sin\theta \\ sin\theta & cos\theta \end{array} \right)
-\left( \begin{array}{ccc} e^{-i\lambda_+z} & 0 \\ 0 & e^{-i\lambda_-z} \end{array} \right)
-\left( \begin{array}{ccc} cos\theta & sin\theta \\ -sin\theta & cos\theta \end{array} \right) \\
-\\
-= \left( \begin{array}{ccc} e_-sin^2\theta + e_+cos^2\theta & (e_+-e_-)sin\theta cos\theta \\ 
-(e_+-e_-)sin\theta cos\theta & e_+sin^2\theta + e_-cos^2\theta \end{array} \right)
-\end{array}
-\end{equation}
-where $e_+$ and $e_-$ are $e^{-i\lambda_+z}$ and $e^{-i\lambda_-z}$ respectively.
-Equation $(13)$ can now give the probability amplitude of the photon and axion fields at any point on the z-axis, simply by inputting the z-coordinate, and this means that the modulus square of the individual matrix elements gives a probability.
-E.g.
-${\left|{M_{12}}\right|}^2 = Prob(p\rightarrow a)$.
-The particular equations that we are interested in are the probability that a photon will couple with an axion, and that an axion will couple with a photon, corresponding to the matrix elements $M_{12}$ and $M_{21}$, which happen to be identical to each other, and equal to
-
-\begin{equation}
-Prob(p\rightarrow a) = Prob(a\rightarrow p) = \left| e_+-e_- \right|^2 sin^2\theta cos^2\theta
-\end{equation}
-
-\subsection{Large and Small Axion Mass Approximations}
-Equation $(15)$ is not of great help, as the exponential terms still depend on both the axion mass and coupling, so it is difficult to directly evaluate the relationship between the two.
-However, we can make large and small mass approximations, where we investigate the behaviour of the equations, if we assume the axion has a very small mass, and if it has a very large mass.
-Before making any approximations, manipulate equation $(15)$ using variations of trigonometric identities, so that $sin^2\theta cos^2\theta$ becomes $\frac{sin^22\theta}{4}$, and convert the exponential terms into a $cos$ term, so it becomes
-
-\begin{equation}
-Prob = \left( 1 - cos[(\lambda_+-\lambda_-)z] \right) \frac{sin^22\theta}{2}
-\end{equation}
-Now the only parts of equation $(16)$ that depend on either the axion mass or the axion coupling are the trigonometric functions, so we can apply the approximations to the $sin^22\theta$, as it is of a higher power.
-By writing
-
-\begin{equation*}
-tan^22\theta = \frac{4B^2\omega^2}{M^2m_a^4} = \frac{sin^22\theta}{cos^22\theta} = \frac{sin^22\theta}{1-sin^22\theta}
-\end{equation*}
-
-we can rearrange for $sin^22\theta$, and write this as a fraction of constants (known and unknown).
-
-\begin{equation}
-sin^22\theta = \frac{4B^2\omega^2}{M^2m_a^4+4B^2\omega^2}
-\end{equation}
-
-This is where an approximation can be introduced.
-If the axion mass, $m_a$, is taken to be very small, $(m_a<<1)$, then $m_a^4$ can be neglected and assumed to be zero.
-This leads to, for small mass, $sin^22\theta \approx 1$.
-If the axion mass is taken to be very large, the $m_a^4$ term becomes very large, $4B^2\omega^2$ can be neglected and $sin^22\theta \approx \frac{4B^2\omega^2}{M^2m_a^4}$.
-When plugged into equation $(16)$, substituting in the constants for ($\lambda_+-\lambda_-$), we get the probability for the small mass limit:
-
-\begin{equation}
-Prob = \frac{1}{2} \left[ 1-cos\left(\frac{m_a^2z}{2\omega cos2\theta} \right) \right]
-\end{equation}
-
-By writing $cos2\theta$ in terms of constants, and again making another small $m_a$ approximation and neglecting a 1, we find $cos2\theta \approx \frac{Mm_a^2}{2B\omega}$, so equation $(18)$ becomes
-
-\begin{equation} Prob = \frac{1}{2} \left[ 1-cos \left(\frac{Bz}{M} \right) \right]
-\end{equation}
-Equation $(19)$ shows that in the small mass limit, the probability that a photon becomes an axion or vice-versa, does not depend at all on the mass of the axion.
-This is convenient as it makes the mass-coupling relationship much easier to plot, simply as a straight line.
-
-In the large mass limit, $sin^22\theta \approx \frac{4B^2\omega^2}{M^2m_a^4}$ so following the same method as for in the low mass limit, but approximating $cos2\theta \approx 1$, we get the result
-
-\begin{equation} Prob = \frac{1}{2} \left[ 1- cos\left(\frac{m_a^2z}{2\omega} \right) \right] \frac{4B^2\omega^2}{M^2m_a^4}
-\end{equation}
-
-\section{Results}
-\label{sec:results}
-
-By using the results published in the 2010 'New ALPS results on hidden-sector lightweights' (this paper will be referred to several times in the results and discussions), we read that the maximum conversion probability from photon, to axion, to photon again is, in the $95\%$ probability limit, $2.25\times10^{-25}$.
-So the probability of a single conversion is the square root of this.
-By using this value in equation $(19)$ and equation $(20)$, we acquire two different relationships between axion mass, $m_a$, and coupling $1/M$, one for a high mass and one for a low mass.
-Figure (2) shows these two relationships plotted on a graph.
-\begin{figure}[h]
-\centering
-\includegraphics[width=1\textwidth]{Images/sokoban_cas_2.png}
-\caption{\label{Graph.jpg} A graph showing the boundary of the relationship between the axion mass and axion coupling.}
-\end{figure}
-
-The left hand side of the graph (the flat line) is a graphical representation of the fact that, if the mass is very small, the coupling becomes independent of the mass of the axion.
-The right hand side of the graph shows that, if the mass is significantly large, the limit becomes dependent on a decaying trigonometric function.
-These results match up with figure 4 from the 'New ALPS results...' paper.
-This line does not, however, represent the only values that the mass and coupling can take,  as we recall that the probability of conversion used is the \textit{maximum} probability.
-Therefore, this line only represents a boundary between possible and im possible combinations of axion mass and coupling values, and rules out any combinations of values that lie above the line.
-Also notice that, for a low mass, figure 2 reads a coupling strength of $\approx 2\times 10^{-8} GeV^{-1} $, whereas, in figure 4 of the ALPS paper previously mentioned, the low mass coupling strength reads to be $\approx 5\times 10^{-7}GeV{-1}$.
-We see, in figure 2 that the large mass approximation starts to have effect at around $10^{-12} GeV$, which matches up very closely with figure 4 of the ALPS paper.
-
-\section{Discussion}
-\label{sec:discussion}
-The difference in the two values for the low mass coupling strength may have been caused by a number of factors.
-Firsly, an assumption has been made, that, because $g \propto 1/M$, $g = 1/M$.
-No account has been made of a possible constant factor in the case where $g$ and $M$ are not directly inversely proportional.
-Another error may have arisen due to the fact that we assumed that the quoted probability, $2.25 \times 10^{-25}$, was the probability that a photon $\rightarrow$ axion $\rightarrow$ photon conversion would take place, where it may have actually been that a single photon $\rightarrow$ axion / axion $\rightarrow$ photon conversion would occur.
-Some small errors may have also been introduced when converting constants, such as the magnetic field or the frequency of light, into electron volts to be in natural units.
-The constants, in natural units, were inputted to only 4 decimal places.
-To improve the accuracy of the values on the graph plotted in figure 2, these constants could be used to many more decimal places, especially when using an accurate program, such as MatLab.
-We must however take figure 2 with a pinch of salt, as there is obviously a large transition step between the small mass and large mass approximations.
-The closer the values are to the transition between the two approximations, the more unreliable the values are, as the original fraction we were using to approximate in equation $(17)$ becomes less dependent on just a single term of the denominator.
-Another assumption that has been made is that the refractive index inside the argon gas is equal to that of a vacuum, $n=1$, whereas the real refractive index is slightly higher than this.
+Initially, the Q-Learning agent struggled to solve the puzzle, requiring approximately 1800 episodes to achieve its first successful completion.
+After this initial breakthrough, the agent demonstrated improved learning efficiency, achieving successful completions in subsequent attempts approximately 60\% of the time.
 
@@
 
-In this experiment, we have theoretically reproduced limits set on the mass and coupling strength of possible axionic particles, by using a series of mathematical calculations and physical and mathematical approximations.
-Our methods and approximations have arrived at a graph which qualitatively matches the most stringent constraints on the existence of axions.
-\\
-In the future, the ALPS collaboration will continue with their research into the properties of axions and other weakly interacting particles, by increasing magnet strength and laser power, to increase the chances of photon $\rightarrow$ axion conversion.
-
 \printbibliography

### 2024-06-22 presentations/article/article.tex
Add search article

@@
 \usepackage{multicol}
-
+\usepackage[nottoc, notlof, notlot]{tocbibind}
+\usepackage[backend=biber, style=authoryear]{biblatex}
 \usepackage{csquotes}
-\usepackage[style=verbose-ibid,backend=biber]{biblatex}
-\bibliography{sample}
 
@@
   J. Tremblay\textsuperscript{1}\thanks{\texttt{jeremy-tremblay@outlook.fr}}  
-  \space et T. Guyomard\textsuperscript{1}\thanks{\texttt{thomas.guyomard@etu.univ-littoral.fr}} \\
+  \space and T. Guyomard\textsuperscript{1}\thanks{\texttt{thomas.guyomard@etu.univ-littoral.fr}} \\
   \textsuperscript{1}Université du Littoral Côte d'Opale, Calais, France
@@
 
-\section{Related Works}
+\section{Related Work}
 
@@
 
-In the realm of real-time strategy games, Vinyals et al.
+In the realm of real-time strategy games, \cite{vinyals2019grandmaster} Vinyals et al.
 (2019) showcased advanced Q-Learning and reinforcement learning methods in achieving Grandmaster level performance in StarCraft II.
@@
 This approach facilitated effective learning and decision-making by the Q-Learning algorithm.
-
 \section{Methodology}
@@
 
-The implementation was conducted using Python programming language, leveraging the Gym Sokoban library.
+The implementation was conducted using the Python programming language, leveraging the Gym Sokoban library.
 Gym Sokoban provides a simulated environment for the Sokoban game, facilitating the integration of reinforcement learning algorithms for experimentation and evaluation.
@@
     \item Pushing a box onto a target: +1.0
-    \item Pushing a box off target: -1.0
+    \item Pushing a box off a target: -1.0
     \item All boxes on targets: +10.0
@@
 We began by implementing Q-Learning on a Sokoban puzzle with three boxes using the Gym Sokoban library in Python.
-The chosen level (Figure \ref{fig:sokoban_level}) is a representative example of Sokoban's complexity, where the agent must strategically move 3 boxes to designated target locations.
+The chosen level (Figure \ref{fig:sokoban_level}) is a representative example of Sokoban's complexity, where the agent must strategically move three boxes to designated target locations.
 
@@
 
-Initially, the Q-Learning agent struggled to solve the puzzle, requiring approximately 1800 episodes to achieve its first successful completion.
-After this initial breakthrough, the agent demonstrated improved learning efficiency, achieving successful completions in subsequent attempts approximately 60\% of the time.
+Initially, the Q-Learning agent struggled to solve the puzzle, requiring approximately 1630 episodes to achieve its first successful completion.
+After this initial breakthrough, the agent demonstrated improved learning efficiency, achieving successful completions in subsequent attempts.
+This performance is described in (Figure \ref{fig:initial_results}).
 
-\section{Conclusions}
-\label{sec:conclusions}
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.49\textwidth]{Images/resultats_initial.png}
+    \caption{Initial results of the Q-Learning algorithm on the Sokoban puzzle.}
+    \label{fig:initial_results}
+\end{figure}
+
+This figure shows the average reward per episode for a game of Sokoban.
+For each simulation, we decided to launch 2000 games to see the results, because we think this amount is relevant to determine if the agent performs correctly or not.
+Initial fluctuations indicate inconsistency, but after the first successful solve (which can be seen with the sudden peak in rewards), rewards stabilize, reflecting improved performance and more frequent wins.
+
+It is also important to note that the execution time for these experiments was relatively long, with each episode taking approximately 1.5 seconds to complete.
+This extended training time is a significant limitation of the Q-Learning algorithm in complex environments like Sokoban.
+
+\subsection{Loss Detection and Penalty}
+
+To improve the agent's performance, we implemented a loss detection mechanism to identify and penalize unsolvable states.
+
+First, we identified three scenarios that could lead to a loss:
+\begin{enumerate}
+    \item A box is stuck in a corner.
+    \item A box is trapped between other boxes but can still be moved if others are shifted.
+    \item No boxes appear stuck, but the overall configuration makes the level unsolvable.
+\end{enumerate}
+
+We focused on detecting the first case, where a box is irreversibly stuck in a corner.
+
+The following pseudo-code illustrates the algorithm for detecting when a box is stuck in a corner:
+
+\begin{verbatim}
+for each box in boxes:
+    if box is in a corner:
+        terminate episode
+        apply penalty of -10 points
+\end{verbatim}
+
+Implementing this detection and penalty improved the agent's performance, as shown in Figure \ref{fig:performance_wall_detection}.
+The agent was able to avoid dead-end situations more effectively, reducing the number of futile episodes and improving the overall learning efficiency.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.49\textwidth,height=6cm]{Images/performance_wall_detection.png}
+    \caption{Performance improvement with loss detection and penalty for boxes stuck in corners.}
+    \label{fig:performance_wall_detection}
+\end{figure}
+
+From this figure, we observe more variations in rewards, which result from penalizing the agent when the game is in a loss state.
+The agent found the optimal path more quickly, around 1500 episodes.
+The execution time has also been reduced to 1.3 seconds per episode due to this improvement.
+
+This improvement helps the agent recognize when it is making mistakes and learn from them.
+
+\subsection{Removing No-Op Action}
+
+To further enhance the agent's performance, we decided to address situations that led to unnecessary actions. We have decided to keep the previous improvements.
+
+In the game of Sokoban, there are several possible actions: moving in each of the four directions and pushing a box in each of the four directions, making a total of eight actions.
+Additionally, there exists an action where the agent does nothing, which can be likened to a human "thinking." However, in the context of AI, this action is redundant as we aim to minimize execution time.
+We noticed that around 20\% of the actions taken by our model in the previous simulation were this one.
+To refine the agent's behavior further, we removed the "no-op" (no operation) action, which did not contribute to solving the puzzle.
+
+The impact of this modification is shown in Figure \ref{fig:performance_no_op}.
+Although the improvement was marginal, the agent's performance showed a slight increase in the number of successful episodes, and it started finding the optimal path around 1400 episodes.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.5\textwidth,height=6cm]{Images/performance_no_op.png}
+    \caption{Performance after removing the no-op action.}
+    \label{fig:performance_no_op}
+\end{figure}
+
+\subsection{Penalizing Invalid Moves}
+
+Building on the previous improvement, we introduced a penalty system to discourage the agent from making invalid moves, such as attempting to push a box where there is none or moving into walls.
+The objective was to enhance the agent's decision-making by penalizing ineffective actions and guiding it towards more productive strategies.
+
+The penalty for these invalid moves was set to -0.5 points.
+However, during our experiments, we observed that the agent was unable to finish the level at all, even once in 2000 episodes, regardless of the penalty value.
+We think that this excessive penalization led to a decline in performance.
+The agent became overly cautious, resulting in reduced exploration and an overall negative impact on its ability to solve the puzzle efficiently.
+Furthermore, this method felt somewhat like guiding our agent through the level.
+
+This suggests that while discouraging invalid moves is important, excessive penalties can hinder the learning process.
+Therefore, this approach was ultimately deemed counterproductive and was abandoned in favor of other methods.
+
+\subsection{Parameter Tuning}
+
+To optimize the Q-Learning performance, we experimented with tuning the algorithm's parameters: $\alpha$ (learning rate), $\gamma$ (discount factor), and $\epsilon$ (exploration rate).
+The default values used were $\alpha = 0.5$, $\gamma = 0.95$, and $\epsilon = 0.1$.
+After a random search, we did not observe any remarkable difference between the parameter values.
+Additionally, we attempted to fine-tune the reward system parameters to better guide the agent's learning process.
+
+The parameter tuning process involved using an optimization algorithm (search tree) to find the best combination of values.
+However, this process proved to be computationally expensive and time-consuming.
+After 16 hours of optimization with a very small number of iterations (20 trials of 2000 steps), the settled parameters were:
+
+\begin{itemize}
+    \item Correct box placement: 8
+    \item Invalid box placement: 0
+    \item Victory: 0
+    \item Defeat: -7
+    \item Step penalty: -0.14972124706419776
+\end{itemize}
+
+At first glance, the results are surprising, but we trained an agent with these settings.
+Despite these efforts, the results were not as expected.
+The agent learned to exploit the reward system by repeatedly moving boxes back and forth to gain points without solving the puzzle.
+This behavior highlighted the difficulty in balancing reward structures and parameter values in Q-Learning.
+
+We think that an execution time of 1.3 seconds per episode is too long to simulate many episodes and find the best parameters.
+We need to find a way to reduce this time to be able to find the best parameters, such as rewriting the code in a faster language like C++.
+
+\subsection{Generalization Issues}
+
+After these unsuccessful attempts, we tested the agent's ability to generalize to new Sokoban levels without complete retraining.
+To do this, we reused the Q-table extracted from the previous best trainings and placed the agent on a new level with the same number of boxes.
+The agent was unable to solve the puzzle efficiently, requiring over 1700 episodes to start solving the puzzle, worse than the initial learning phase.
+
+This experience indicated that the state representation, tied to the entire map, was too specific and did not promote generalization.
+We think a better approach would be to use a more general state representation that can be used on different levels, such as representing only a 5x5 square around the agent.
+This would allow the agent to generalize its learning to different levels, even though finding the optimal path could be more challenging.
+Another solution would be to represent only the boxes, targets, and the agent, omitting the walls.
+There are many possibilities, and we think a mix of approaches could yield good results, offering a path for future research.
+
+We then deeply investigated whether we could consider our model "stable" once it had learned to solve the puzzle.
+We wanted to check if it made many mistakes even after successfully completing the level in the past.
+We reported the number of games won and lost after the first victory on the same level to observe changes.
+Figure \ref{fig:number_of_game_won} shows the results of this experiment.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.5\textwidth]{Images/number_of_game_won.png}
+    \caption{Number of games won or lost after the first victory.}
+    \label{fig:number_of_game_won}
+\end{figure}
+
+The first bar in the figure shows the games lost and ended by our program, where the agent stuck a box in a corner.
+The second bar represents the number of games won by the agent, and the last bar shows the games lost by the agent (after 200 iterations).
+We can see that the agent finishes the level about 2 times out of 7.
+
+We observe that the agent is not stable at all; it has difficulty solving the puzzle even after the first successful game.
+We think we can address this issue by using a decreasing epsilon to make the agent explore more at the beginning and exploit more when it has already learned the optimal path.
+
+\section{Discussion}
+
+In conclusion, our study demonstrates the challenges and potential of applying Q-Learning to the game of Sokoban.
+Despite various modifications, including end-game detection, action refinement, and parameter tuning, the performance improvements were limited and highlighted significant areas for further research.
+
+Future work should focus on optimizing the code for faster execution, enabling more extensive parameter tuning without prohibitive computational costs.
+Additionally, comparing Q-Learning with other models such as Monte Carlo Tree Search (MCTS) and Deep Q-Learning (DQL) could provide valuable insights into more efficient learning strategies.
+
+Finally, exploring smaller state representations could help improve the agent's ability to generalize across different levels.
+By addressing these aspects, we can enhance the effectiveness of reinforcement learning algorithms in complex environments like Sokoban.
 

### 2024-06-22 presentations/article/article.tex
Add references

@@
 \usepackage{graphicx}
+\setlength{\marginparwidth}{2cm}
 \usepackage[colorinlistoftodos]{todonotes}
@@
 \usepackage{csquotes}
+
+\addbibresource{references.bib} % Specify the bibliography file
 
@@
 Mnih et al.
-(2013) pioneered the use of deep Q-Learning to learn game policies directly from pixel inputs, achieving human-level performance on multiple classic Atari games.
+(2013) \cite{mnih2013playing} pioneered the use of deep Q-Learning to learn game policies directly from pixel inputs, achieving human-level performance on multiple classic Atari games.
 
-In the realm of real-time strategy games, \cite{vinyals2019grandmaster} Vinyals et al.
-(2019) showcased advanced Q-Learning and reinforcement learning methods in achieving Grandmaster level performance in StarCraft II.
+In the realm of real-time strategy games, Vinyals et al.
+(2019) \cite{vinyals2019grandmaster} showcased advanced Q-Learning and reinforcement learning methods in achieving Grandmaster level performance in StarCraft II.
 Their work exemplifies the application of sophisticated learning algorithms to master complex strategic environments.
@@
 These studies highlight the versatility of Q-Learning in adapting to diverse gaming dynamics, from classic Atari games to complex real-time strategy scenarios like StarCraft II.
-In contrast, the challenges specific to Sokoban, such as sparse rewards and intricate state transitions, remain less explored.
-This study aims to address these challenges and enhance Q-Learning's applicability in puzzle-solving domains.
+In contrast, the challenges specific to Sokoban, such as sparse rewards and intricate state transitions, remain less explored although we can cite the work of Sébastien Racanière et al.
+(2017) \cite{racaniere2017imagination} on the subject of reinforcement learning.
+This study aims to address these challenges in puzzle-solving domains.
 
@@
 
-The implementation was conducted using the Python programming language, leveraging the Gym Sokoban library.
+The implementation was conducted using the Python programming language, leveraging the Gym Sokoban \cite{SchraderSokoban2018} library.
 Gym Sokoban provides a simulated environment for the Sokoban game, facilitating the integration of reinforcement learning algorithms for experimentation and evaluation.
@@
     \centering
-    \includegraphics[width=0.5\textwidth,height=6cm]{Images/performance_no_op.png}
+    \includegraphics[width=0.49\textwidth,height=6cm]{Images/performance_no_op.png}
     \caption{Performance after removing the no-op action.}
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{Images/number_of_game_won.png}
-    \caption{Number of games won or lost after the first victory.}
+    \includegraphics[width=0.49\textwidth]{Images/number_of_game_won.png}
+    \caption{Number of endgame types after first win.}
     \label{fig:number_of_game_won}

### 2024-06-22 presentations/presentation_mars/presentation_mars.tex

--- 2024-06-21 presentations/presentation_fevrier/presentation_fevrier.tex
@@
 \section{Références}
-
 \begin{frame}
@@
 
+    \begin{thebibliography}{9}
+
+        \bibitem{racaniere2018imagination}
         Sébastien Racanière, Théophane Weber, David P.
-Reichert, Lars Buesing, Arthur Guez, Danilo Rezende, Adria Puigdomènech Badia, Oriol Vinyals, Nicolas Heess, Yujia Li, Razvan Pascanu, Peter Battaglia, Demis Hassabis, David Silver, Daan Wierstra, "Imagination-Augmented Agents for Deep Reinforcement Learning", DeepMind, arXiv:1707.06203v2 [cs.LG] 14 Feb 2018
+Reichert, Lars Buesing, Arthur Guez, Danilo Rezende, Adria Puigdomènech Badia, Oriol Vinyals, Nicolas Heess, Yujia Li, Razvan Pascanu, Peter Battaglia, Demis Hassabis, David Silver, Daan Wierstra.
+        \newblock Imagination-Augmented Agents for Deep Reinforcement Learning.
+        \newblock \textit{DeepMind}, arXiv:1707.06203v2 [cs.LG], 14 Feb 2018.
 
+        \bibitem{SchraderSokoban2018}
+        Max-Philipp B. Schrader.
+        \newblock gym-sokoban.
+        \newblock GitHub repository, GitHub, 2018.
+        \newblock \url{https://github.com/mpSchrader/gym-sokoban}.
+
+    \end{thebibliography}
 \end{frame}
@@
 %------------------------------------------------
-\section{Ajout d'un mécanisme de renforcement}
-
-\begin{frame}{Ajout d'un mécanisme de renforcement}
-    \begin{itemize}
-        \item \textbf{Application du renforcement au jeu du Sokoban}
-            \begin{itemize}
-                \item L'agent (IA) apprend à jouer au Sokoban en interagissant avec l'environnement.
-                \item Les récompenses définies pour différentes actions guident l'agent vers des comportements souhaités.
-            \end{itemize}
-        \item \textbf{Mise en application du Q-Learning}
-            \begin{itemize}
-                \item La Q-table est mise à jour itérativement en fonction des récompenses obtenues.
-                \item L'agent utilise la Q-table pour choisir ses actions et optimiser sa politique de choix au fil du temps.
-            \end{itemize}
-    \end{itemize}
-\end{frame}
-%------------------------------------------------
 \section{Implémentation du Q-learning}
@@
 
+    \begin{block}{Contenu de la Q-table}
+        \textcolor{blue}{\texttt{1146848432601504200: array([-0.05, 2.77913742, 1.69800543, 3.03067097, 2.54018055, 2.77913742, 2.77913742, 3.03067097, 2.54018055])}}
+    \end{block}
+
 \end{frame}
+
 %------------------------------------------------
-
-\section{Intégration du système de récompense}
+\section{Résultats du Q-learning}
 
 \begin{frame}
-	\frametitle{Intégration du système de récompense}
+    \frametitle{Résultats du Q-learning (1/6)}
+    \begin{columns}
+        \begin{column}{0.4\textwidth}
+            \begin{figure}
+                \centering
+                \includegraphics[width=\textwidth]{Images/imagejeux.png}
+                \caption{Évolution des récompenses totales obtenues par épisode.}
+            \end{figure}
+        \end{column}
+        \begin{column}{0.4\textwidth}
+            \textbf{Contexte de jeu :}\\
+            \begin{itemize}
+                \item[$\bullet$] Niveau de taille moyenne
+                \item[$\bullet$] Jeu de 10x10 cases
+                \item[$\bullet$] 3 caisses à pousser
+            \end{itemize}
+            \vspace{0.5cm}
+            \textbf{Contexte d'exécution :}\\
+            \begin{itemize}
+                \item[$\bullet$] 10 000 parties réalisées
+                \item[$\bullet$] Utilisation d'un algorithme de Q-learning 
+                \item[$\bullet$] 8h30 de temps d'exécution au total
+            \end{itemize}
+        \end{column}
+    \end{columns}
+\end{frame}
 
-	\begin{block}{Objectif}
-		Introduire un système de récompenses permettant de guider l'agent vers les actions optimales grâce à des récompenses positives et des pénalités.
+\begin{frame}
+    \frametitle{Résultats du Q-learning (2/6)}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.7\textwidth]{Images/resultat2.png}
+        \caption{Évolution du nombre de caisses poussées en dehors des emplacements par épisode.}
+		\begin{block}{Observation des résultats}
+			\small L'agent a tendance à pousser une ou deux caisses en dehors des emplacements par épisode.
 		\end{block}
+    \end{figure}
+\end{frame}
 
-	\smallskip % Vertical whitespace
-
-	\begin{center}
-        \begin{tabular}{|c|c|}
-            \hline
-            \textbf{Action} & \textbf{Récompense} \\
-            \hline
-            Effectuer une action & -0.1 \\
-            Pousser une boîte sur la cible & 1.0 \\
-            Pousser une boîte hors de la cible & -1.0 \\
-            Achever le niveau & 10.0 \\
-            \hline
-        \end{tabular}
-    \end{center}
-
-	\begin{block}{Pour aller plus loin...}
-		Pénalités en cas de caisses bloquées.
+\begin{frame}
+    \frametitle{Résultats du Q-learning (3/6)}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.75\textwidth]{Images/resultat4.png}
+        \caption{Évolution du nombre de caisses poussées sur un emplacement par épisode.}
+    \end{figure}
+	\begin{block}{Observation des résultats}
+        \footnotesize L'agent a compris qu'il devait pousser des caisses sur un emplacement.
     \end{block}
@@
 
-%------------------------------------------------
-
-\section{Résultats}
+\begin{frame}
+    \frametitle{Résultats du Q-learning (4/6)}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.8\textwidth]{Images/resultat3.png}
+        \caption{Évolution du nombre d'inactions par épisode.}
+    \end{figure}
+	\begin{block}{Observation des résultats}
+        \small L'agent a compris que les mouvements blancs étaient inutiles.
+    \end{block}
+\end{frame}
 
 \begin{frame}
-	\frametitle{Résultats}
+    \frametitle{Résultats du Q-learning (5/6)}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.8\textwidth]{Images/resultat1.png}
+		\caption{Évolution des récompenses totales obtenues par épisode.}
+    \end{figure}
+	\begin{block}{Observation des résultats}
+        \small Changement de comportement : Exploration $\rightarrow$ Exploitation.
+    \end{block}
 
-	\begin{itemize}
-        \item \textbf{Un temps d'exécution élevé} Concernant la génération des niveaux.
-        \item \textbf{Des performances faibles...} Valeurs des récompenses négatives à la fin de l'execution et constantes: -300.
-        \item \textbf{Des niveaux différents} Rendant l'apprentissage caduc.
-        \item \textbf{Représentation de la partie} On cherche à récupérer un visuel du jeu afin de réaliser un I2A et d'améliorer le système de récompenses.
-    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Résultats du Q-learning (6/6)}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.9\textwidth]{Images/resultat_2000.png}
+		\caption{Résultats du Q-learning sur 2000 épisodes.}
+    \end{figure}
 \end{frame}
@@
 			\hline
-            1 & Résolution des probleme de performances et apprentissage plus poussé. \\
+            1 & Exploiter notre implémentation du deep Q-learning et comparer les résultats avec ceux du Q-learning.  \\
             \hline
-            2 & Comparaison des performances avec des modèles comme MCTS pour évaluer l'efficacité relative. \\
+            2 & Finaliser le MCTS et analyser les résultats.  \\
             \hline
-            3 & Si possible, explorer la possibilité d'utiliser les représentations visuelles de Gym Sokoban pour enrichir la planification. \\
+            3 & Explorer la possibilité d'utiliser les représentations visuelles de Gym Sokoban pour enrichir la planification. \\
             \hline
@@
             \hline
-            5 & Analyser les performances de chaque approche, en mettant en évidence les forces et les faiblesses dans le contexte de Sokoban. \\
+            5 & Si possible, analyser les performances de chaque approche, en mettant en évidence les forces et les faiblesses dans le contexte de Sokoban. \\
             \hline

### 2024-06-22 presentations/presentation_juin/presentation_juin.tex

--- 2024-06-22 presentations/presentation_mars/presentation_mars.tex
@@
 %------------------------------------------------
-\section{Agents Augmentés par l'Imagination}
-
-\begin{frame}
-	\frametitle{Agents Augmentés par l'Imagination \ / (I2A)}
-
-	\smallskip % Vertical whitespace
-
-	\begin{definition}
-	\alert{L'apprentissage par renforcement avec augmentation par l'imagination} appelée \alert{I2A} est une approche du domaine de l'intelligence artificielle permettant d'améliorer la prise de décision des agents d'apprentissage.
-	Les agents combinent l'apprentissage automatique avec et sans modèles avec des générations de scénarios pour anticiper des situations inédites et proposer des solutions optimales.
-	\end{definition}
-
-	\smallskip % Vertical whitespace
-
-\end{frame}
-
-%------------------------------------------------
 
@@
 \end{frame}
-
 %------------------------------------------------
-\section{Résultats du Q-learning}
 
 \begin{frame}
-    \frametitle{Résultats du Q-learning (1/6)}
+    \frametitle{Contexte et environement d'exécution}
     \begin{columns}
@@
             \begin{itemize}
-                \item[$\bullet$] 10 000 parties réalisées
-                \item[$\bullet$] Utilisation d'un algorithme de Q-learning 
-                \item[$\bullet$] 8h30 de temps d'exécution au total
+                \item[$\bullet$] 2000 parties réalisées/algorithme
+                \item[$\bullet$] Utilisation du Q-learning 
+                \item[$\bullet$] 40 min de temps d'exécution au total/algorithme
             \end{itemize}
@@
 
+%------------------------------------------------
 \begin{frame}
-    \frametitle{Résultats du Q-learning (2/6)}
-    \begin{figure}
-        \centering
-        \includegraphics[width=0.7\textwidth]{Images/resultat2.png}
-        \caption{Évolution du nombre de caisses poussées en dehors des emplacements par épisode.}
-		\begin{block}{Observation des résultats}
-			\small L'agent a tendance à pousser une ou deux caisses en dehors des emplacements par épisode.
-		\end{block}
-    \end{figure}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Résultats du Q-learning (3/6)}
-    \begin{figure}
-        \centering
-        \includegraphics[width=0.75\textwidth]{Images/resultat4.png}
-        \caption{Évolution du nombre de caisses poussées sur un emplacement par épisode.}
-    \end{figure}
-	\begin{block}{Observation des résultats}
-        \footnotesize L'agent a compris qu'il devait pousser des caisses sur un emplacement.
-    \end{block}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Résultats du Q-learning (4/6)}
-    \begin{figure}
-        \centering
-        \includegraphics[width=0.8\textwidth]{Images/resultat3.png}
-        \caption{Évolution du nombre d'inactions par épisode.}
-    \end{figure}
-	\begin{block}{Observation des résultats}
-        \small L'agent a compris que les mouvements blancs étaient inutiles.
-    \end{block}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Résultats du Q-learning (5/6)}
-    \begin{figure}
-        \centering
-        \includegraphics[width=0.8\textwidth]{Images/resultat1.png}
-		\caption{Évolution des récompenses totales obtenues par épisode.}
-    \end{figure}
-	\begin{block}{Observation des résultats}
-        \small Changement de comportement : Exploration $\rightarrow$ Exploitation.
-    \end{block}
-
-\end{frame}
-
-\begin{frame}
-    \frametitle{Résultats du Q-learning (6/6)}
+    \frametitle{Premiers résultats du Q-learning}
     \begin{figure}
@@
 \end{frame}
+%------------------------------------------------
+
+\begin{frame}
+    \frametitle{Détection de partie perdue}
+    \begin{itemize}
+        \item \textbf{Meilleures performances :} Optimiser l'algorithme de jeu pour détecter plus rapidement les situations de blocage.
+        \item \textbf{Pénalités :} Réduire les erreurs de détection et minimiser les faux positifs.
+    \end{itemize}
+
+    \frametitle{Problème}
+    \begin{block}{Problématique}
+        Comment détecter efficacement une partie perdue dans le jeu Sokoban ?
+    \end{block}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Cas Simple}
+    \begin{block}{Observation des résultats}
+        \small L'agent a bloqué la caisse contre le mur.
+    \end{block}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.5\textwidth]{Images/sokoban_cas_1.png}
+    \end{figure}
+\end{frame}
 
 %------------------------------------------------
-\section{Plan de Travail}
+\begin{frame}
+    \frametitle{Cas plus complexe}
+    \begin{figure}
+        \centering
+        \begin{block}{Observation des résultats}
+			\small L'agent a bloqué une caisse entre deux autres caisses .
+		\end{block}
+        \includegraphics[width=0.5\textwidth]{Images/sokoban_cas_2.png}
 
-\begin{frame}{Plan de Travail}
+    \end{figure}
+\end{frame}
+%------------------------------------------------
+\begin{frame}
+    \frametitle{Cas très complexe}
+    \begin{figure}
+        \centering
+        \begin{block}{Observation des résultats}
+			\small Aucune caisse n'est bloqué pour autant la partie est perdue.
+		\end{block}
+        \includegraphics[width=0.5\textwidth]{Images/sokoban_cas_3.png}
+
+    \end{figure}
+\end{frame}
+%------------------------------------------------
+
+\begin{frame}
+    \frametitle{Fonction : vérifier\_fin\_de\_partie}
+
+    \begin{enumerate}
+        \item Pour chaque case du plateau :
+        \begin{itemize}
+            \item Si c'est une caisse :
+            \begin{itemize}
+                \item Si la caisse est bloquée dans un coin:
+                \item La partie est perdue.
+            \end{itemize}
+            \item Vérifier si la caisse peut être poussée :
+            \begin{enumerate}
+                \item Pour chaque direction (haut, bas, gauche, droite) :
+                \item Si la case derrière la caisse et celle devant sont libres :
+                \item La caisse peut être poussée. La partie n'est pas perdue.
+            \end{enumerate}
+            \item Si la caisse ne peut pas être poussée :
+            \begin{itemize}
+                \item Rechercher les caisses adjacentes.
+                \item Si aucune caisse adjacente n'est trouvée :
+                \item La partie est perdue.
+                \item Si des caisses adjacentes sont trouvées :
+                \item Appliquer récursivement la fonction vérifier\_fin\_de\_partie pour chaque caisse adjacente.
+            \end{itemize}
+        \end{itemize}
+        \item Si on est arrivé ici alors la caisse peut être poussée, renvoyer vrai.
+    \end{enumerate}
+\end{frame}
+
+%------------------------------------------------
+\section{Résultats du Q-learning}
+
+%------------------------------------------------
+\begin{frame}
+    \frametitle{Résultats du Q-learning avec détection des murs (1/4)}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.6\textwidth]{results/q_learning_dict_with_wall_detection/q_learning_dict_with_wall_detection.png}
+    \end{figure}
+\end{frame}
+%------------------------------------------------
+\begin{frame}
+    \frametitle{Résultats du Q-learning avec détection des murs avec actions obligatoires (2/4)}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.6\textwidth]{results/q_learning_dict_with_wall_detection_with_no_empty_actions/figures.png}
+    \end{figure}
+\end{frame}
+%------------------------------------------------
+\begin{frame}
+    \frametitle{Résultats du Q-learning avec pénalité en cas d'actions inutiles (3/4)}
+    \begin{block}{Idée :}
+        \small Mettre une pénalité en cas d'action inutile (foncer dans un mur, essayer de pousser une caisse invisible...)
+    \end{block}
+    \begin{block}{Résultats :}
+        \small L'agent ne termine jamais le niveau, malgrés plusieurs valeurs de malus (de -1 à -0.2)
+    \end{block}
+\end{frame}
+%------------------------------------------------
+\begin{frame}
+    \frametitle{Résultats du Q-learning avec détection des murs, actions obligatoires et mise à jour des récompenses (4/4)}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.6\textwidth]{results/q_learning_dict_with_wall_detection_with_no_empty_actions_with_reward/Figure_1.png}
+    \end{figure}
+
+\end{frame}
+
+%------------------------------------------------
+\begin{frame}
+    \frametitle{Recherche des meilleurs paramètres pour $\alpha$, $\gamma$ et $\epsilon$}
+
+    \begin{itemize}
+        \item Alpha ($\alpha$) : Le taux d'apprentissage
+        \item Gamma ($\gamma$) : Le facteur de remise
+        \item Epsilon ($\epsilon$) : Le taux d'exploration 
+    \end{itemize}
+
+    \begin{block}{Exécution d'un algorithme de recherche par optimisation (arbre de recherche)}
+        Problème : durée d'exécution de 16 heures pour 20 itérations. \\
+        Utilisation des valeurs récupérées : résultat peu concluant, le nombre d'itérations n'est probablement pas significatif.
+    \end{block}
+
+    \begin{block}{Hyperparamètres}
+        Meilleurs paramètres : \{'alpha': 0.30000000000000004, 'gamma': 0.95, 'epsilon': 0.30000000000000004\}
+    \end{block}
+\end{frame}
+
+%------------------------------------------------
+\begin{frame}[shrink=10]
+    \frametitle{Recherche des meilleurs paramètres pour le système de récompense}
+
+    \begin{block}{Exécution d'un algorithme de recherche par optimisation (arbre de recherche)}
+        Durée d'exécution : 12 heures 20 minutes sur 20 instances.
+    \end{block}
+
+    \begin{block}{Meilleures valeurs de récompense trouvées}
+        \begin{itemize}
+            \item Récompense placement correct de boîte : 8
+            \item Récompense placement invalide de boîte : 0
+            \item Récompense de victoire : 0
+            \item Récompense de défaite : -7
+            \item Récompense de mouvement invalide : -1
+            \item Récompense à chaque itération : -0.14972124706419776
+        \end{itemize}
+    \end{block}
+
+    \begin{block}{Résultats}
+        L'agent pousse la boîte sur un emplacement à l'infini...
+    \end{block}
+\end{frame}
+
+%------------------------------------------------
+\section{Suite logique de ces travaux de recherche}
+
+\begin{frame}{Suite logique de ces travaux de recherche}
     \begin{table}
@@
             \hline
-            1 & Exploiter notre implémentation du deep Q-learning et comparer les résultats avec ceux du Q-learning.  \\
+            1 &  Réaliser un algorithme de détection de fin de partie et l'optimiser à l'aide d'un autre langage (C++), et / ou recoder la bibliothèque du jeu.\\
             \hline
-            2 & Finaliser le MCTS et analyser les résultats.  \\
+            2 &  Rechercher les meilleurs paramètres possibles pour le système de récompense et pour l'exploration.\\
             \hline
-            3 & Explorer la possibilité d'utiliser les représentations visuelles de Gym Sokoban pour enrichir la planification. \\
+            3 & Tester l'agent sur des nouveaux niveaux. \\
             \hline
-            4 & Tester l'agent sur différents niveaux afin d'évaluer sa capacité de généralisation. \\
-            \hline
-            5 & Si possible, analyser les performances de chaque approche, en mettant en évidence les forces et les faiblesses dans le contexte de Sokoban. \\
+            4 & Essayer de nouveaux modèles tel que le Deep Q-learning et les réseaux de neurones convolutionnels et les comparer. \\
             \hline

### 2024-06-22 presentations/presentation_decembre/presentation_decembre.tex
Merge Search article into main

--- 2024-06-21 presentations/presentation_fevrier/presentation_fevrier.tex
@@
 \usepackage[yyyymmdd]{datetime}
+\usepackage[french]{babel}
 
@@
 
-\title[Initation Recherche]{Création de différentes IA en utilisant une architecture I2A} % The short title in the optional parameter appears at the bottom of every slide, the full title in the main parameter is only on the title page
+\title[Initation Recherche]{Création de diffférentes IA en utilisant une architecture I2A} % The short title in the optional parameter appears at the bottom of every slide, the full title in the main parameter is only on the title page
 
@@
 
-\institute[]{Université du Littoral Côte d'Opale\\ \smallskip \textit{Encadrant : Jérôme Buisine}} % Your institution, the optional parameter can be used for the institution shorthand and will appear on the bottom of every slide after author names, while the required parameter is used on the title slide and can include your email address or additional information on separate lines
+\institute[]{Université du Littoral Côte d'Opale\\ \smallskip \textit{Encadrant : M.
+Jérôme Buisine}} % Your institution, the optional parameter can be used for the institution shorthand and will appear on the bottom of every slide after author names, while the required parameter is used on the title slide and can include your email address or additional information on separate lines
 
@@
 
-	Jeu de \alert{réflexion}. Le but : le joueur doit ranger des caisses sur des cases cibles.
-	\smallskip % Vertical whitespace
+	Jeu de \alert{réflexion}. le joueur doit ranger des caisses sur des cases cibles.
+	\bigskip % Vertical whitespace
 
 	\begin{itemize}
-		\item Le personnage a la capacité d'effectuer des déplacement dans chacune des 4 directions possibles. Le niveau est validé une fois toutes les caisses rangées.
+		\item Le personnage peut réaliser neuf opérations :
+        \begin{itemize}
+            \item 4 opérations concernent le déplacement dans une case adjacente à lui (droite, gauche, haut, bas).
+            \item 4 opérations concernent l'action de pousser une caisse sur une case adjacente à lui dans la direction de son mouvement (droite, haut, gauche, bas), sauf si celle-ci est bloquée par un obstacle quelconque.
+            \item La dernière action vide : ne rien faire.
+		\end{itemize}
 	\end{itemize}
 
-	\smallskip % Vertical whitespace
+	\bigskip % Vertical whitespace
 
-	\begin{figure}
-		\includegraphics[width=0.2\linewidth]{Images/sokaibanfailed2.png}
-		\caption{Capture d'écran du jeu Sokoban.}
-	\end{figure}
+	Une fois toutes les caisses rangées le niveau est validé et ainsi de suite jusqu'à la fin de tout les niveaux.
 
@@
 
+%------------------------------------------------
+\section{Environnement d'étude}
+
+\begin{frame}
+	\frametitle{Environnement d'étude}
+
+	\begin{columns}[c] % The "c" option specifies centered vertical alignment while the "t" option is used for top vertical alignment
+		\begin{column}{0.45\textwidth} % Left column width
+			\textbf{Environnement de travail}
+			\begin{enumerate}
+				\item Python
+				\item Gym
+				\item Plusieurs modes de jeu
+			\end{enumerate}
+		\end{column}
+		\begin{column}{0.5\textwidth} % Right column width
+
+		\begin{figure}
+			\centering
+			\includegraphics[width=0.9\linewidth]{Images/sokoban.png}
+			\caption{Capture d'écran du jeu Sokoban}
+		\end{figure}
+		\end{column}
+	\end{columns}
+\end{frame}
 %------------------------------------------------
@@
 %------------------------------------------------
-
-\section{IA Q-learning avec une représentation en tableau}
+\section{Fonctionnement des Agents Augmentés par Imagination}
 
 \begin{frame}
-	\frametitle{IA Q-learning avec une représentation en tableau}
+	\frametitle{Fonctionnement des Agents Augmentés par Imagination}
+
+	\smallskip % Vertical whitespace
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=1.0\linewidth]{Images/schema_i2a.png}
+		\caption{Schéma récapitulatif de l'approche I2A.}
+	\end{figure}
+
+	\smallskip % Vertical whitespace
+
+\end{frame}
+
+%------------------------------------------------
+\section{Performances de différents modèles}
+
+\begin{frame}
+	\frametitle{Performances de différents modèles}
+
+	\smallskip % Vertical whitespace
+
+	\begin{block}{Informations}
+		Les différents modèles ne performent pas de la même manière au jeu du Sokoban.
+	\end{block}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=0.65\linewidth]{Images/sokoban_performance.png}
+		\caption{Schéma représentant les succès de différents modèles au jeu du sokoban.}
+	\end{figure}
+
+	\smallskip % Vertical whitespace
+
+\end{frame}
+
+%------------------------------------------------
+\section{Comparaison d'efficacité de l'imagination}
+
+\begin{frame}{Comparaison d'efficacité de l'imagination}
+    \begin{columns}
+        \begin{column}{\textwidth}
+            \begin{table}
+                \centering
+                \begin{tabular}{l|ccccccc}
+                    Boxes & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
+                    \hline
+                    I2A (\%) & 99.5 & 97 & 92 & 87 & 77 & 66 & 53 \\
+                    Standard (\%) & 97 & 87 & 72 & 60 & 47 & 32 & 23 \\
+					\caption{Généralisation de I2A à des environnements avec différents nombres de boîtes.}
+                \end{tabular}
+
+            \end{table}
+
+            \begin{table}
+                \centering
+                \begin{tabular}{l|ccccccc}
+                    I2A@87 & $\sim$ 1400 \\
+                    I2A MC search @95 & $\sim$ 4000 \\
+                    MCTS@87 & $\sim$ 25000 \\
+                    MCTS@95 & $\sim$ 100000 \\
+                    Random search & $\sim$ millions \\
+                \end{tabular}
+				\caption{Efficacité de l'imagination pour différentes architectures.}
+            \end{table}
+        \end{column}
+    \end{columns}
+\end{frame}
+
+%------------------------------------------------
+
+\section{Q-learning avec une représentation en tableau}
+
+\begin{frame}
+	\frametitle{Q-learning avec une représentation en tableau}
 
 	\begin{block}{Definitions}
-		L'implémentation combine le Q-learning avec un modèle interne I2A pour résoudre le problème complexe du Sokoban, un jeu de réflexion.
+		Le Q-learning facilite les décisions séquentielles.
+Grâce à un tableau, chaque cellule stocke la valeur Q, qui est mise à jour lorsqu'un agent prend une action dans un état donné qui aide ainsi à l'amélioration petit à petit de la politique de prise de décision.
 	\end{block}
@@
 	\begin{figure}
-		\includegraphics[width=0.5\linewidth]{Images/q_learning.png}
+		\includegraphics[width=0.4\linewidth]{Images/q_learning.png}
 		\caption{Schéma du fonctionnement du Q-Learning.}
@@
 %------------------------------------------------
-\section{Ajout d'un mécanisme de renforcement}
 
-\begin{frame}{Ajout d'un mécanisme de renforcement}
-    \begin{itemize}
-        \item \textbf{Application du renforcement au jeu du Sokoban}
-            \begin{itemize}
-                \item L'agent (IA) apprend à jouer au Sokoban en interagissant avec l'environnement.
-                \item Les récompenses définies pour différentes actions guident l'agent vers des comportements souhaités.
-            \end{itemize}
-        \item \textbf{Mise en application du Q-Learning}
-            \begin{itemize}
-                \item La Q-table est mise à jour itérativement en fonction des récompenses obtenues.
-                \item L'agent utilise la Q-table pour choisir ses actions et optimiser sa politique de choix au fil du temps.
-            \end{itemize}
-    \end{itemize}
-\end{frame}
-%------------------------------------------------
-\section{Implémentation du Q-learning}
+\section{Deep Q-Learning avec un réseau de neurones}
 
 \begin{frame}
-	\frametitle{Implémentation du Q-learning}
+	\frametitle{Deep Q-Learning avec un réseau de neurones}
 
-	\begin{itemize}
-        \item \textbf{Q-table} Contient les états / actions du jeu, elle est initialisée avec des zéros.
-        \item \textbf{Boucle d'apprentissage} Itérations sur des épisodes pour mettre à jour la Q-table.
-        \item \textbf{Système de récompenses} Intégration des récompenses conformément à la politique définie.
-        \item \textbf{Mise à jour de la \textbf \textit Q-table} Prise en compte de la récompense immédiate et de l'estimation de la récompense future.
-        \item \textbf{Exploration et Exploitation} Equilibre les connaissances actuelles et permet davantage d'apprentissage.
-    \end{itemize}
-
-\end{frame}
-%------------------------------------------------
-
-\section{Intégration du système de récompense}
-
-\begin{frame}
-	\frametitle{Intégration du système de récompense}
-
-	\begin{block}{Objectif}
-		Introduire un système de récompenses permettant de guider l'agent vers les actions optimales grâce à des récompenses positives et des pénalités.
+	\begin{block}{Definitions}
+		Le \alert{Deep Q-Learning} est une extension de Q-Learning qui utilise des réseaux de neurones profonds pour gérer des d'états et d'actions plus importants que le Q-Learning classique.
 	\end{block}
@@
 
-	\begin{center}
-        \begin{tabular}{|c|c|}
-            \hline
-            \textbf{Action} & \textbf{Récompense} \\
-            \hline
-            Effectuer une action & -0.1 \\
-            Pousser une boîte sur la cible & 1.0 \\
-            Pousser une boîte hors de la cible & -1.0 \\
-            Achever le niveau & 10.0 \\
-            \hline
-        \end{tabular}
-    \end{center}
+	\begin{figure}
+		\includegraphics[width=0.5\linewidth]{Images/deep_q_learning.png}
+		\caption{Schéma du fonctionnement du Deep Q-Learning.}
+	\end{figure}
 
-	\begin{block}{Pour aller plus loin...}
-		Pénalités en cas de caisses bloquées.
-	\end{block}
 \end{frame}
@@
 %------------------------------------------------
-
-\section{Résultats}
+\section{Parallèle entre Sokoban et les I2A}
 
 \begin{frame}
-	\frametitle{Résultats}
+	\frametitle{Parallèle entre Sokoban et les I2A}
+
+	\begin{block}{Objectifs}
+		Objectif : entraîner un agent étant en capacité de jouer et d'évoluer dans le jeu du Sokoban.
+		Problématique : Comment l'I2A peut-elle être appliquée pour guider les actions dans un environnement complexe ?
+	\end{block}
+
+	\smallskip % Vertical whitespace
 
 	\begin{itemize}
-        \item \textbf{Un temps d'exécution élevé} Concernant la génération des niveaux.
-        \item \textbf{Des performances faibles...} Valeurs des récompenses négatives à la fin de l'execution et constantes: -300.
-        \item \textbf{Des niveaux différents} Rendant l'apprentissage caduc.
-        \item \textbf{Représentation de la partie} On cherche à récupérer un visuel du jeu afin de réaliser un I2A et d'améliorer le système de récompenses.
+		\item 9 actions mais une infinités de cartes de tailles différentes et parfois plusieurs solutions possibles.
+		\item Il faut adapter les concepts de l'I2A au jeu du Sokoban afin d'obtenir un modèle performant.
+		\item Plan d'action : 
+		\begin{itemize}
+			\item Distillation de la politique pour combiner apprentissage sans modèle et avec modèle.
+			\item Utilisation de l'imagination pour guider les actions dans l'environnement.
+			\item Ajout de visuels de l'environnement du jeu avec traitement d'image afin d'améliorer les résultats.
 		\end{itemize}
+	\end{itemize}
+
 \end{frame}
@@
             \hline
-            1 & Résolution des probleme de performances et apprentissage plus poussé. \\
+            1 & Compréhension et test de l'environnement Gym Sokoban. \\
             \hline
-            2 & Comparaison des performances avec des modèles comme MCTS pour évaluer l'efficacité relative. \\
+            2 & Recherche et compréhension des différentes approches (Q-learning, MCTS, Deep Q-Learning). \\
             \hline
-            3 & Si possible, explorer la possibilité d'utiliser les représentations visuelles de Gym Sokoban pour enrichir la planification. \\
+            3 & Développement de différents modèles d'apprentissage automatique (Q-learning, Deep Q-learning...). \\
             \hline
-            4 & Tester l'agent sur différents niveaux afin d'évaluer sa capacité de généralisation. \\
+            4 & Utilisation de l'approche I2A dans notre jeu. \\
             \hline
-            5 & Analyser les performances de chaque approche, en mettant en évidence les forces et les faiblesses dans le contexte de Sokoban. \\
+            5 & Comparaison des performances avec des modèles comme MCTS pour évaluer l'efficacité relative. \\
+            \hline
+            6 & Si possible, explorer la possibilité d'utiliser les représentations visuelles de Gym Sokoban pour enrichir la planification. \\
+            \hline
+            7 & Tester l'agent sur différents niveaux afin d'évaluer sa capacité de généralisation. \\
+            \hline
+            8 & Analyser les performances de chaque approche, en mettant en évidence les forces et les faiblesses dans le contexte de Sokoban. \\
             \hline
@@
 \end{frame}
+%------------------------------------------------
+\section{AUTRE}
+
 %----------------------------------------------------------------------------------------

### 2024-06-22 src/functions.py

@@ -1,0 +1,159 @@
+import os
+import pickle
+import csv
+import random
+import numpy as np
+import matplotlib.pyplot as plt
+
+def seed_everything(seed, env):
+    random.seed(seed)
+    np.random.seed(seed)
+    env.seed(seed)
+
+UP = 'up'
+DOWN = 'down'
+LEFT = 'left'
+RIGHT = 'right'
+PUSH_UP = 'push_up'
+PUSH_DOWN = 'push_down'
+PUSH_LEFT = 'push_left'
+PUSH_RIGHT = 'push_right'
+
+def determine_agent_position(board):
+    for i, room in enumerate(board):
+        for j, cell in enumerate(room):
+            if cell in [5, 6]:
+                return i, j
+            
+def determine_direction_based_on_action(action):
+    if action == 0:
+        return UP
+    elif action == 1:
+        return DOWN
+    elif action == 2:
+        return LEFT
+    elif action == 3:
+        return RIGHT
+    elif action == 4:
+        return PUSH_UP
+    elif action == 5:
+        return PUSH_DOWN
+    elif action == 6:
+        return PUSH_LEFT
+    elif action == 7:
+        return PUSH_RIGHT
+    else:
+        return None
+
+def can_push_box(board, x, y, direction):
+    rows, cols = board.shape
+    if direction == PUSH_UP:
+        if x - 1 >= 0 and board[x - 1][y] in [1, 2, 5, 6] and board[x - 2][y] in [1, 2, 5, 6]:
+            return True
+    elif direction == PUSH_DOWN:
+        if x + 1 < rows and board[x + 1][y] in [1, 2, 5, 6] and board[x + 2][y] in [1, 2, 5, 6]:
+            return True
+    elif direction == PUSH_LEFT:
+        if y - 1 >= 0 and board[x][y - 1] in [1, 2, 5, 6] and board[x][y - 2] in [1, 2, 5, 6]:
+            return True
+    elif direction == PUSH_RIGHT:
+        if y + 1 < cols and board[x][y + 1] in [1, 2, 5, 6] and board[x][y + 2] in [1, 2, 5, 6]:
+            return True
+    return False
+
+def can_agent_move(board, x, y, direction):
+    rows, cols = board.shape
+    if direction == UP:
+        if x - 1 >= 0 and board[x - 1][y] in [1, 2, 5, 6]:
+            return True
+    elif direction == DOWN:
+        if x + 1 < rows and board[x + 1][y] in [1, 2, 5, 6]:
[…]

### 2024-06-22 src/q_learning_dict_with_wall_detection_with_no_empty_actions_test_best_hyper_parameters.py

@@ -1,0 +1,93 @@
+import gym
+import gym_sokoban
+import numpy as np
+import optuna
+from functions import *
+from multiprocessing import cpu_count
+
+def train_agent(trial):
+    alpha = trial.suggest_float('alpha', 0.1, 0.9, step=0.2)
+    gamma = trial.suggest_float('gamma', 0.8, 0.99, step=0.05)
+    epsilon = trial.suggest_float('epsilon', 0.1, 0.5, step=0.1)
+    num_episodes = 1000  
+
+    env = gym.make('Sokoban-v0')
+    seed_everything(42, env)
+
+    q_table = {}
+    rewards_per_episode = []
+    episode_at_first_win = None
+    is_current_game_lost = 1
+
+    for i_episode in range(num_episodes):
+        seed_everything(42, env)
+        state = env.reset(render_mode='tiny_rgb_array')
+        done = False
+        total_reward = 0
+        is_current_game_lost = 1
+
+        while not done:
+            index = hash(int(''.join(map(str, env.env.env.room_state.flatten()))))
+            given_reward = -0.1
+
+            if index not in q_table:
+                q_table[index] = np.zeros(env.action_space.n - 1)
+
+            if np.all(q_table[index] == q_table[index][0]):
+                action = env.action_space.sample() - 1
+                while action == -1:
+                    action = env.action_space.sample() - 1
+            elif np.random.uniform(0, 1) < epsilon:
+                action = env.action_space.sample() - 1
+                while action == -1:
+                    action = env.action_space.sample() - 1
+            else:
+                action = np.argmax(q_table[index])
+
+            next_state, game_reward, done, info = env.env.env.step(action, observation_mode='tiny_rgb_array')
+
+            futur_index = hash(int(''.join(map(str, env.env.env.room_state.flatten()))))
+            if futur_index not in q_table:
+                q_table[futur_index] = np.zeros(env.action_space.n - 1)
+
+            if game_reward == 0.9:
+                given_reward += 1
+            elif game_reward == -1.1:
+                given_reward += -1
+            elif game_reward > 2:
+                is_current_game_lost = 0
+                if episode_at_first_win is None:
+                    episode_at_first_win = i_episode
+                given_reward += 10
+                done = True
+
+            if determine_direction_based_on_action(action) in [PUSH_UP, PUSH_DOWN, PUSH_LEFT, PUSH_RIGHT] and is_game_lost(env.env.env.room_state):
+                given_reward += -10
[…]

### 2024-06-22 src/q_learning_dict_with_wall_detection_with_no_empty_actions_with_reward.py

@@ -1,0 +1,108 @@
+import gym
+import gym_sokoban
+import numpy as np
+from functions import *
+
+env = gym.make('Sokoban-v0')
+observation = env.reset()
+seed_everything(42, env)
+
+q_table = {}
+
+alpha = 0.5
+gamma = 0.95
+epsilon = 0.1
+num_episodes = 2000
+
+reward_box_placed = 10  # Récompense pour placer une boîte sur un emplacement cible
+reward_box_moved = -1    # Récompense pour déplacer une boîte loin d'un emplacement cible
+reward_default = -0.1    # Récompense par défaut pour les actions autres que placer ou déplacer des boîtes
+
+rewards_per_episode = []
+boxes_placed_per_episode = []
+boxes_moved_per_episode = []
+waiting_moves_per_episode = []
+games_lost_per_episode = []
+episode_at_first_win = None
+
+for i_episode in range(num_episodes):
+    seed_everything(42, env)
+    state = env.reset(render_mode='tiny_rgb_array')
+    done = False
+
+    total_reward = 0
+    boxes_placed = 0
+    boxes_moved = 0
+    wainting_moves = 0
+    is_current_game_lost = 1
+    number_of_moves = 0
+
+    while not done:
+        index = hash(int(''.join(map(str, env.env.env.room_state.flatten()))))
+        given_reward = reward_default
+
+        if not index in q_table:
+            q_table[index] = np.zeros(env.action_space.n - 1)
+
+        if np.all(q_table[index] == q_table[index][0]):
+            action = env.action_space.sample() - 1
+            while (action == -1):
+                action = env.action_space.sample() - 1
+
+        elif random.uniform(0, 1) < epsilon:
+            action = env.action_space.sample() - 1
+            while (action == -1):
+                action = env.action_space.sample() - 1
+        else:
+            action = np.argmax(q_table[index])
+            # print(f"Action took: {action}")
+            
+        if action == -1:
+            wainting_moves += 1
+
+        next_state, game_reward, done, info = env.env.env.step(action, observation_mode='tiny_rgb_array')
+        number_of_moves += 1
+            
+        futur_index = hash(int(''.join(map(str, env.env.env.room_state.flatten()))))
+        if not futur_index in q_table:
+            q_table[futur_index] = np.zeros(env.action_space.n - 1)
+
+        if game_reward == 0.9:
+            boxes_placed += 1
+            given_reward = reward_box_placed
[…]

### 2024-06-22 presentations/article/article.tex
Add README file
Fix typo

@@
 
+\DeclareCiteCommand{\citeauthoryear}
+  {\boolfalse{citetracker}%
+   \boolfalse{pagetracker}%
+   \usebibmacro{prenote}}
+  {\ifciteindex
+     {\indexnames{labelname}}
+     {}%
+   \printnames{labelname}%
+   \setunit{\addspace}\printtext{\bibopenparen}%
+   \printfield{year}\bibcloseparen}
+  {\multicitedelim}
+  {\usebibmacro{postnote}}
+
 \addbibresource{references.bib} % Specify the bibliography file
@@
   J. Tremblay\textsuperscript{1}\thanks{\texttt{jeremy-tremblay@outlook.fr}}  
-  \space and T. Guyomard\textsuperscript{1}\thanks{\texttt{thomas.guyomard@etu.univ-littoral.fr}} \\
+  \space and T. Guyomard\textsuperscript{1}\thanks{\texttt{thomas.guyomard.pro@orange.fr}} \\
   \textsuperscript{1}Université du Littoral Côte d'Opale, Calais, France
@@
 Previous studies have demonstrated the effectiveness of Q-Learning and deep reinforcement learning techniques in various gaming environments.
-Mnih et al.
-(2013) \cite{mnih2013playing} pioneered the use of deep Q-Learning to learn game policies directly from pixel inputs, achieving human-level performance on multiple classic Atari games.
+\textcite{mnih2013playing} pioneered the use of deep Q-Learning to learn game policies directly from pixel inputs, achieving human-level performance on multiple classic Atari games.
 
-In the realm of real-time strategy games, Vinyals et al.
-(2019) \cite{vinyals2019grandmaster} showcased advanced Q-Learning and reinforcement learning methods in achieving Grandmaster level performance in StarCraft II.
+In the realm of real-time strategy games, \textcite{vinyals2019grandmaster} showcased advanced Q-Learning and reinforcement learning methods in achieving Grandmaster level performance in StarCraft II.
 Their work exemplifies the application of sophisticated learning algorithms to master complex strategic environments.
@@
 These studies highlight the versatility of Q-Learning in adapting to diverse gaming dynamics, from classic Atari games to complex real-time strategy scenarios like StarCraft II.
-In contrast, the challenges specific to Sokoban, such as sparse rewards and intricate state transitions, remain less explored although we can cite the work of Sébastien Racanière et al.
-(2017) \cite{racaniere2017imagination} on the subject of reinforcement learning.
+In contrast, the challenges specific to Sokoban, such as sparse rewards and intricate state transitions, remain less explored although we can cite the work of \textcite{racaniere2017imagination} on the subject of reinforcement learning.
 This study aims to address these challenges in puzzle-solving domains.
@@
 
-The implementation was conducted using the Python programming language, leveraging the Gym Sokoban \cite{SchraderSokoban2018} library.
+The implementation was conducted using the Python programming language, leveraging the \textcite{SchraderSokoban2018} library.
 Gym Sokoban provides a simulated environment for the Sokoban game, facilitating the integration of reinforcement learning algorithms for experimentation and evaluation.
